---
title: "Novel vs. repeated choice project: Behavioral data checks"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(here)
theme_set(theme_bw())
helpers_path = here()
```

# YN Task

```{r}
data_yn = read.csv(paste0(helpers_path, '/inputs/data_choiceYN.csv'))
```

Columns according to a readme file:

| Column      | Description |
| ----------- | ----------- |
| subnum | Subject Number |
| day | day number |
| week | week number |
| stimNum  | stimulus number, each stimulus has a identification number |
| stimLettNum | number of the combination of letters in the stimulus, each letter combination has a identification number |
| type  | stimulus' type:   0  == regular exposure; 1  == hypertrained |
| orientation  | orientation angle of the grid |
| filling  | amount of angle filled with color |
| shape | shape number |
| valueO | value in weight of the orientation |
| valueF | value in weight of the filling |
| valueS | value in weight of the shape |
| session | session number |
| yesChosen  | 1 if yes is chosen 0 otherwise |
| response | number of response button for left arrow or right arrow |
| payoff | payoff from trial |
| possiblePayoff | possible payoff from stimulus if yes chosen |
| reference | value of reference amount (if no chosen) can be 0 50 or -50 |
| rt | response time |
| fmri | 1 if the subject was in the scanner during that trial, 0 otherwise |

Not in the data that's read in even though it's listed above

| stimLettNum |

Additional columns without descriptions

| inizialTime | 
| endTime | 
| inizialTimeResp | 
| endTimeResp | 
| startFix | 
| evtimeON | 
| evtimeOFF | 
| crossON | 

```{r}
names(data_yn)
```

## Visits and number of trials

6 unique subjects

```{r}
unique(data_yn$subnum)
```

Up to 11 sessions per subject

```{r}
unique(data_yn$day)
```

All subjects have 800 trials (4 blocks) of the YN task on each day

```{r}
with(data_yn, table(subnum, day))
```

```{r}
unique(data_yn$week)
```

All subjects are missing a fourth session in the last week (what should have been visit 12)

```{r}
with(data_yn, table(subnum, week))
```

## Unique stims

There are 726 unique stimuli used (6 shapes x 11 orientations x 11 filling weights)

```{r}
length(unique(data_yn$stimNum))
```

How many unique stimuli does each subject see? Only one subjects sees all stims. Others see almost all of them.

```{r}
data_yn %>%
  group_by(subnum) %>%
  summarise(num_unique_stims = length(unique(stimNum)))
```
## Stim types

On each day each subject encounters 480 HT stimuli and 320 RE stimuli

```{r}
with(data_yn, table(subnum, day, type))
```

Each subject has their unique set of 12 HT stimuli.

```{r}
data_yn %>%
  filter(type == 1) %>%
  group_by(subnum) %>%
  summarise(ht_stims = unique(stimNum), .groups="keep")
```
## Stims by features

```{r}
unique(data_yn$orientation)
```

```{r}
length(unique(data_yn$orientation))
```

0 and 90 are the most common orientations

```{r}
table(data_yn$orientation)
```

Subjects have differing frequencies of each orientation

```{r}
with(data_yn, table(subnum, orientation))
```

```{r}
unique(data_yn$filling)
```

*There are 9 unique filling values (not 11)*

```{r}
length(unique(data_yn$filling))
```

0 is the most common filling weight followed by |0.4|

```{r}
table(data_yn$filling)
```

Subjects have differing frequencies of each filling weight. 0 is most common for all but the rest of the order is not the same across subjects.

```{r}
with(data_yn, table(subnum, filling))
```

```{r}
with(data_yn, table(orientation, filling))
```

```{r}
unique(data_yn$shape)
```

```{r}
table(data_yn$shape)
```

```{r}
with(data_yn, table(subnum, shape))
```

```{r}
with(data_yn, table(orientation, filling, shape))
```

```{r}
unique(data_yn$valueO)
```

```{r}
length(unique(data_yn$valueO))
```

```{r}
table(data_yn$valueO)
```

75 degrees has a value of 0. The further away the orientation from 75 the larger the gain/loss.

```{r}
with(data_yn, table(valueO, orientation))
```

```{r}
unique(data_yn$valueF)
```

```{r}
length(unique(data_yn$valueF))
```

```{r}
table(data_yn$valueF)
```

Filling weight 0 has 0 value and the further away from 0 has larger gain/loss. All filling weights are associated with one absolute value except for filling weight |0.4| which can have a value of |0.4| or |0.6|.

```{r}
with(data_yn, table(valueF, filling))
```

```{r}
unique(data_yn$valueS)
```

```{r}
length(unique(data_yn$valueS))
```

```{r}
table(data_yn$valueS)
```

```{r}
with(data_yn, table(valueS, shape))
```

## Session (Run)

There is an error in the session column.

```{r}
unique(data_yn$session)
```

One session 3 is mis-assigned to -99.

```{r}
table(data_yn$session)
```

**Subject 621 does not have session 3 on day 11.**

```{r}
with(data_yn, table(subnum, session))
```

```{r}
data_yn_clean = data_yn %>%
  filter(session != -99)
```

What exactly are these sessions compared with `day` and `week` columns? They are runs. Subjects complete 4 runs of 200 trials per visit.

```{r}
with(data_yn_clean, table(session, week))
```

```{r}
with(data_yn, table(session, day))
```

## Choice

Choice data is missing for one run so looking at choice only in dataset that excludes run 3 of day 11 for subnum 621.

```{r}
unique(data_yn_clean$yesChosen)
```


```{r}
table(data_yn_clean$yesChosen)
```

Choice data is missing/mis-coded for the same run 

```{r}
with(data_yn_clean, table(subnum, yesChosen))
```

```{r}
unique(data_yn_clean$response)
```

```{r}
table(data_yn_clean$response)
```

```{r}
with(data_yn_clean, table(fmri,response))
```

## Payoff

```{r}
length(unique(data_yn_clean$payoff))
```

```{r}
length(unique(data_yn_clean$possiblePayoff))
```

## Reference value

```{r}
unique(data_yn_clean$reference)
```

```{r}
table(data_yn_clean$reference)
```

```{r}
with(data_yn_clean, table(subnum, reference))
```

```{r}
with(data_yn_clean, table(subnum, day, reference))
```

```{r}
with(data_yn_clean, table(subnum, session, reference))
```

There are the same number of trials for each reference value in the scanner across subjects but these are not equally distributed across subjects. A third of the subjects have seen all reference values in the scanner while the other two thirds have either not seen the 50 or -50 in the scanner.

```{r}
with(data_yn_clean, table(subnum, reference, fmri))
```

## fMRI trials

```{r}
with(data_yn_clean, table(subnum, session, fmri))
```

All subjects have 400 trials (2 runs) per each of the 3 fmri visits

```{r}
with(data_yn_clean, table(subnum, day, fmri))
```

Subjects completed 2nd to 4th sesssions in the scanner, never the first session.

```{r}
with(data_yn_clean %>% filter(fmri==1), table(subnum, session, day))
```

## RT

Any negative RTs? No.

```{r}
sum(data_yn_clean$rt< 0)
```

```{r}
summary(data_yn_clean$rt)
```

There are some trials with very long RTs

```{r}
data_yn_clean %>%
  filter(rt>5) %>%
  ggplot(aes(rt))+
  geom_histogram(alpha=0.5, bins=30)+
  theme(panel.grid = element_blank())+
  facet_wrap(~subnum)+
  xlab("")+
  labs(title="RT>5s trials")
```
Number of trials with longer than 5 s RTs for each subject across visits.

```{r}
with(data_yn_clean %>% filter(rt>5), table(subnum, day))
```

Proportion of all trials with RT > 5s

```{r}
nrow(data_yn_clean %>% filter(rt>5))/nrow(data_yn_clean)
```

What proportion of slow trials is from each subject?

```{r}
round(with(data_yn_clean %>% filter(rt>5), table(subnum))/nrow(data_yn_clean %>% filter(rt>5)), 3)
```

## Blank columns

```{r}
unique(data_yn$inizialTime)
```

```{r}
unique(data_yn$endTime)
```

```{r}
unique(data_yn$inizialTimeResp)
```

```{r}
unique(data_yn$endTimeResp)
```

Drop the above columns without data

```{r}
data_yn_clean = data_yn_clean %>%
  select(-inizialTime, -inizialTimeResp, -endTime, -endTimeResp)
```

## Columns with no description

This is probably when each trial began but I don't know what it is in reference to.

```{r}
length(unique(data_yn_clean$startFix))
```

These are presumably eye-tracking data for fmri trial but no idea what units they are in or what the reference is. I'll keep them but can't use them for any analysis yet.

```{r}
length(unique(data_yn_clean$evtimeON))
```

```{r}
length(unique(data_yn_clean$evtimeOFF))
```

```{r}
length(unique(data_yn_clean$crossON))
```

# BC Task

```{r}
data_bc = read.csv(paste0(helpers_path, '/inputs/data_choiceBC.csv'))
```

Columns according to a readme file:

| Column      | Description |
| ----------- | ----------- |
| subnum | Subject Number |
| day | day number | 
| week | week number | 
| stimNumLeft | stimulus on the left number, each stimulus has a identification number | 
| stimNumRight | stimulus on the right number, each stimulus has a identification number | 
| stimLettNumLeft | number of the combination of letters in the stimulus on the left, each letter combination has a identification number | 
| stimLettNumRight | number of the combination of letters in the stimulus on the right, each letter combination has a identification number | 
| TypeLeft | stimulus' type on the left:   0  == regular exposure; 1  == hypertrained | 
| TypeRight | type of stimulus on the right | 
| OrientationLeft | orientation angle of the grid for stimulus of the left | 
| FillingLeft | amount of angle filled with color for stimulus of the left | 
| ShapeLeft | shape in the stimulus of the left | 
| valueOLeft | value in weight of the orientation for stimulus of the left | 
| valueFLeft | value in weight of the filling for stimulus of the left | 
| valueSLeft | value in weight of the shape on the right |  
| OrientationRight | orientation angle of the grid for stimulus of the right | 
| FillingRight | amount of angle filled with color for stimulus of the right | 
| ShapeRight | shape in the stimulus of the right | 
| valueORight | value in weight of the orientation for stimulus of the right | 
| valueFRight | value in weight of the filling for stimulus of the right | 
| valueSRight | value in weight of the shape on the right |  
| leftChosen | 1 if left option is chosen 0 otherwise | 
| Response | number of response button for left arrow or right arrow | 
| Payoff | payoff from trial | 
| possiblePayoffLeft | possible payoff from stimulus on the left | 
| possiblePayoffRight | possible payoff from stimulus on the right | 
| Rt | response time |  
| fmri | 1 if the subject was in the scanner during that trial, 0 otherwise | 

Additional columns without descriptions

| inizialTime | 
| endTime | 
| inizialTimeResp | 
| endTimeResp | 
| startFix | 
| evtimeON | 
| evtimeOFF | 
| crossON | 

```{r}
names(data_bc)
```

## Visits and number of trials

6 unique subjects

```{r}
unique(data_bc$subnum)
```

Up to 11 sessions per subject

```{r}
unique(data_bc$day)
```

All subjects have 200 trials of the BC task on each day

```{r}
with(data_bc, table(subnum, day))
```

```{r}
unique(data_bc$week)
```

All subjects are missing a fourth session in the third week (what should have been visit 12)

```{r}
with(data_bc, table(subnum, week))
```

## Unique stims

There are 726 unique stimuli used (6 shapes x 11 orientations x 11 filling weights) on each side

```{r}
length(unique(data_bc$stimNumLef))
```

```{r}
length(unique(data_bc$stimNumRight))
```

How many unique stimuli does each subject see? 

```{r}
data_bc %>%
  group_by(subnum) %>%
  summarise(num_unique_left_stims = length(unique(stimNumLef)),
            num_unique_right_stims = length(unique(stimNumRight)))
```

## Redundant stim num columns

```{r}
sum(data_bc$stimLettNumLeft == data_bc$stimNumLef) == nrow(data_bc)
```

```{r}
sum(data_bc$stimLettNumRight == data_bc$stimNumRight) == nrow(data_bc)
```

Drop redundant columns and fix column name

```{r}
data_bc_clean = data_bc %>%
  select(-stimLettNumLeft, -stimLettNumRight) %>%
  rename(stimNumLeft = stimNumLef)
```

## Stim types

On each day each subject encounters 66 HT stimuli and 134 RE stimuli

```{r}
with(data_bc, table(subnum, day, typeLeft))
```

```{r}
with(data_bc, table(subnum, day, typeRight))
```

Are pairs of same type (ie. choice is either between two HT stimuli or two RE stimuli)? Yes.

```{r}
with(data_bc, sum(typeLeft == typeRight)) == nrow(data_bc)
```

## Stims by features

## Session (Run)

## Choice

## Payoff

## fMRI trials

## RT

## Blank columns

```{r}
unique(data_bc$inizialTime)
```

```{r}
unique(data_bc$endTime)
```

```{r}
unique(data_bc$inizialTimeResp)
```

```{r}
unique(data_bc$endTimeResp)
```

Drop blank columns

```{r}
data_bc_clean = data_bc_clean %>%
  select(-inizialTime, -inizialTimeResp, -endTime, -endTimeResp)
```

## Columns with no description

This is probably when each trial began but I don't know what it is in reference to.

```{r}
length(unique(data_bc_clean$startFix))
```

These are presumably eye-tracking data for fmri trial but no idea what units they are in or what the reference is. I'll keep them but can't use them for any analysis yet.

```{r}
length(unique(data_bc_clean$evtimeON))
```

```{r}
length(unique(data_bc_clean$evtimeOFF))
```

```{r}
length(unique(data_bc_clean$crossON))
```
