---
title: "Novel vs. repeated choice project: Psychometrics"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(here)
theme_set(theme_bw())
helpers_path = paste0(here(),'/analysis/helpers/')
source(paste0(helpers_path, '01_clean_behavioral_data.R'))
fig_out_path = paste0(here(), '/outputs/fig/')
```

Add columns that will be used for plots below.

```{r}
data_yn_clean = data_yn_clean %>%
  mutate(correct = ifelse(possiblePayoff>reference & yesChosen == 1, 1, ifelse(possiblePayoff < reference & yesChosen == 0, 1, 0))) %>%
  mutate(type = ifelse(type == 1, "HT", "RE"),
         week = ifelse(week == 1, "Week 1", ifelse(week == 2, "Week 2", ifelse(week == 3, "Week 3", NA))),
         week = factor(week, levels = c("Week 1", "Week 2", "Week 3"))) %>%
  mutate(val_diff = possiblePayoff - reference,
         val_diff_bin = round(val_diff/50),
         val_diff_bin_str = paste0(val_diff_bin*50-25,":",val_diff_bin*50+25),
         val_diff_bin_str = factor(val_diff_bin_str, levels = c("-225:-175", "-175:-125", "-125:-75", "-75:-25", "-25:25", "25:75", "75:125", "125:175", "175:225")))

data_bc_clean = data_bc_clean %>%
  mutate(correct = ifelse(possiblePayoffleft>possiblePayoffright & leftChosen == 1, 1, ifelse(possiblePayoffleft<possiblePayoffright & leftChosen == 0, 1, 0))) %>%
  mutate(type = ifelse(typeLeft == 1, "HT", "RE"),
         week = ifelse(week == 1, "Week 1", ifelse(week == 2, "Week 2", ifelse(week == 3, "Week 3", NA))),
         week = factor(week, levels = c("Week 1", "Week 2", "Week 3"))) %>%
  mutate(val_diff = possiblePayoffleft - possiblePayoffright,
         val_diff_bin = round(val_diff/50),
         val_diff_bin_str = paste0(val_diff_bin*50-25,":",val_diff_bin*50+25),
         val_diff_bin_str = factor(val_diff_bin_str, levels = c("-275:-225","-225:-175", "-175:-125", "-125:-75", "-75:-25", "-25:25", "25:75", "75:125", "125:175", "175:225", "225:275"))) %>%
  filter(!is.na(val_diff_bin_str))
```

# Accuracy over days

## YN Task

```{r}
p = data_yn_clean %>%
  group_by(subnum, day, type) %>%
  summarise(mean_correct = mean(correct),
            .groups="keep") %>%
  ungroup() %>%
  group_by(day, type) %>%
  summarise(sem_correct = sd(mean_correct)/sqrt(n()),
            mean_correct = mean(mean_correct), .groups="keep") %>%
  ggplot(aes(day, mean_correct, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_correct-sem_correct, ymax=mean_correct+sem_correct), width=0, size = 1)+
  geom_line()+
  labs(x = "Day", y = "Accuracy", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks=seq(1,11,1))+
  scale_color_brewer(palette = "Dark2")+
 scale_y_continuous(breaks=seq(.75,1,.1), limits = c(.75,1))

p
# ggsave(file=paste0(fig_out_path, 'yn_group_accuracyOverDays.jpg'), p, height = 5, width=8, units="in")
```

```{r}
p = data_yn_clean %>%
  group_by(subnum, day, type) %>%
  summarise(mean_correct = mean(correct),
            sem_correct = sd(correct)/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(day, mean_correct, color=type))+
  geom_point()+
  geom_errorbar(aes(ymin=mean_correct-sem_correct, ymax=mean_correct+sem_correct), width=0)+
  geom_line()+
  facet_wrap(~subnum)+
  labs(x = "Day", y = "Accuracy", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks=seq(1,11,1))+
  scale_color_brewer(palette = "Dark2")
p
# ggsave(file=paste0(fig_out_path, 'yn_accuracyOverDays.jpg'), p, height = 5, width=8, units="in")
```

## BC Task

```{r}
p = data_bc_clean %>%
  group_by(subnum, day, type) %>%
  summarise(mean_correct = mean(correct),
            .groups="keep") %>%
  ungroup() %>%
  group_by(day, type) %>%
  summarise(sem_correct = sd(mean_correct)/sqrt(n()),
            mean_correct = mean(mean_correct), .groups="keep") %>%
  ggplot(aes(day, mean_correct, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_correct-sem_correct, ymax=mean_correct+sem_correct), width=0, size = 1)+
  geom_line()+
  labs(x = "Day", y = "Accuracy", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks=seq(1,11,1))+
  scale_color_brewer(palette = "Dark2")+
 scale_y_continuous(breaks=seq(.75,1,.1), limits = c(.75,1))

p
# ggsave(file=paste0(fig_out_path, 'bc_group_accuracyOverDays.jpg'), p, height = 5, width=8, units="in")
```

```{r}
p = data_bc_clean %>%
  group_by(subnum, day, type) %>%
  summarise(mean_correct = mean(correct),
            sem_correct = sd(correct)/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(day, mean_correct, color=type))+
  geom_point()+
  geom_errorbar(aes(ymin=mean_correct-sem_correct, ymax=mean_correct+sem_correct), width=0)+
  geom_line()+
  facet_wrap(~subnum)+
  labs(x = "Day", y = "Accuracy", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks=seq(1,11,1))+
  scale_color_brewer(palette = "Dark2")

p
# ggsave(file=paste0(fig_out_path, 'bc_accuracyOverDays.jpg'), p, height = 5, width=8, units="in")
```

# Accuracy depending on value difference

## YN Task

```{r}
p = data_yn_clean %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_correct = mean(correct),
            .groups="keep") %>%
  ungroup() %>%
  group_by(week, val_diff_bin_str, type) %>%
  summarise(sem_correct = sd(mean_correct)/sqrt(n()),
            mean_correct = mean(mean_correct), .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_correct, color=type))+
  geom_point(size = 2.5)+
  # geom_jitter(width=.2)+
  geom_errorbar(aes(ymin=mean_correct-sem_correct, ymax=mean_correct+sem_correct), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_grid(.~week)+
  labs(x = "Value Stim - Value Reference", y = "Accuracy", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(.6,1,.2), limits = c(.6, 1))

p
# ggsave(file=paste0(fig_out_path, 'yn_group_accuracyByValDiff.jpg'), p, height = 3, width=9, units="in")
```

```{r}
p = data_yn_clean %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_correct = mean(correct),
            sem_correct = sd(correct)/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_correct, color=type))+
  geom_point()+
  # geom_jitter(width=.2)+
  geom_errorbar(aes(ymin=mean_correct-sem_correct, ymax=mean_correct+sem_correct), width=0)+
  geom_line(aes(group=type))+
  facet_grid(subnum~week)+
  labs(x = "Value Stim - Value Reference", y = "Accuracy", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(.6,1,.2), limits = c(.6, 1))

p
# ggsave(file=paste0(fig_out_path, 'yn_accuracyByValDiff.jpg'), p, height = 7, width=8, units="in")
```

## BC Task

```{r}
p = data_bc_clean %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_correct = mean(correct),
            .groups="keep") %>%
  ungroup() %>%
  group_by(week, val_diff_bin_str, type) %>%
  summarise(sem_correct = sd(mean_correct)/sqrt(n()),
            mean_correct = mean(mean_correct), .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_correct, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_correct-sem_correct, ymax=mean_correct+sem_correct), width=0, size=1)+
  geom_line(aes(group=type))+
  facet_grid(.~week)+
  labs(x = "Value Left - Value Right", y = "Accuracy", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("","-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225",""))+
  scale_y_continuous(breaks = seq(.6,1,.2), limits = c(.6, 1))

p
# ggsave(file=paste0(fig_out_path, 'bc_group_accuracyByValDiff.jpg'), p, height = 3, width=9, units="in")

```

```{r}
p = data_bc_clean %>%
  filter(abs(val_diff_bin) != 6) %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_correct = mean(correct),
            sem_correct = sd(correct)/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_correct, color=type))+
  geom_point()+
  # geom_jitter(width=.2)+
  geom_errorbar(aes(ymin=mean_correct-sem_correct, ymax=mean_correct+sem_correct), width=0)+
  geom_line(aes(group=type))+
  facet_grid(subnum~week)+
  labs(x = "Value Left - Value Right", y = "Accuracy", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("","-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225",""))+
  scale_y_continuous(breaks = seq(.25,1,.25))

p
# ggsave(file=paste0(fig_out_path, 'bc_accuracyByValDiff.jpg'), p, height = 7, width=8, units="in")

```

# Yes/Left depending on value difference

## YN Task

```{r}
p = data_yn_clean %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_yes = mean(yesChosen),
            .groups="keep") %>%
  ungroup() %>%
  group_by(week, val_diff_bin_str, type) %>%
  summarise(sem_yes = sd(mean_yes)/sqrt(n()),
            mean_yes = mean(mean_yes), .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_yes, color=type))+
  geom_hline(aes(yintercept=.5), color="gray")+
  geom_vline(aes(xintercept=5), color="gray")+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_yes-sem_yes, ymax=mean_yes+sem_yes), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_grid(.~week)+
  labs(x = "Value Stim - Value Reference", y = "p(Yes)", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(0,1,.5))

p
# ggsave(file=paste0(fig_out_path, 'yn_group_pYesByValDiff.jpg'), p, height = 3, width = 9, units="in")
```

```{r}
p = data_yn_clean %>%
  group_by(subnum, day, val_diff_bin_str, type) %>%
  summarise(mean_yes = mean(yesChosen),
            .groups="keep") %>%
  ungroup() %>%
  group_by(day, val_diff_bin_str, type) %>%
  summarise(sem_yes = sd(mean_yes)/sqrt(n()),
            mean_yes = mean(mean_yes), .groups="keep") %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 2", "Day 3", "Day 4", "Day 5", "Day 6", "Day 7", "Day 8", "Day 9", "Day 10", "Day 11"))) %>%
  ggplot(aes(val_diff_bin_str, mean_yes, color=type))+
  geom_hline(aes(yintercept=.5), color="gray")+
  geom_vline(aes(xintercept=5), color="gray")+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_yes-sem_yes, ymax=mean_yes+sem_yes), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_wrap(~day)+
  labs(x = "Value Stim - Value Reference", y = "p(Yes)", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(0,1,.5))

p
# ggsave(file=paste0(fig_out_path, 'yn_group_pYesByValDiffByDay.jpg'), p, height = 6, width = 10, units="in")
```

```{r}
p = data_yn_clean %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_yes = mean(yesChosen),
            sem_yes = sd(yesChosen)/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_yes, color=type))+
  # geom_point()+
  geom_jitter(width=.2)+
  geom_errorbar(aes(ymin=mean_yes-sem_yes, ymax=mean_yes+sem_yes), width=0)+
  geom_line(aes(group=type))+
  facet_grid(subnum~week)+
  geom_hline(aes(yintercept=.5), color="gray", linetype = "longdash")+
  geom_vline(aes(xintercept=5), color="gray", linetype = "longdash")+
  labs(x = "Value Stim - Value Reference", y = "p(Yes)", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(0,1,.5))

p
# ggsave(file=paste0(fig_out_path, 'yn_pYesByValDiff.jpg'), p, height = 7, width=8, units="in")
```

```{r}
p = data_yn_clean %>%
  filter(fmri==1) %>%
  group_by(subnum, day, val_diff_bin_str, type) %>%
  summarise(mean_yes = mean(yesChosen),
            sem_yes = sd(yesChosen)/sqrt(n()),
            .groups="keep") %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels  = c("Day 3", "Day 7", "Day 11"))) %>%
  ggplot(aes(val_diff_bin_str, mean_yes, color=type))+
  # geom_point()+
  geom_jitter(width=.2)+
  geom_errorbar(aes(ymin=mean_yes-sem_yes, ymax=mean_yes+sem_yes), width=0)+
  geom_line(aes(group=type))+
  facet_grid(subnum~day)+
  geom_hline(aes(yintercept=.5), color="gray", linetype = "longdash")+
  geom_vline(aes(xintercept=5), color="gray", linetype = "longdash")+
  labs(x = "Value Stim - Value Reference", y = "p(Yes)", title="Y/N Task (fMRI sessions)", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(0,1,.5))

p
# ggsave(file=paste0(fig_out_path, 'yn_pYesByValDiffMRI.jpg'), p, height = 7, width=8, units="in")
```

## BC Task

```{r}
p = data_bc_clean %>%
  filter(abs(val_diff_bin) != 6) %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_left = mean(leftChosen),.groups="keep") %>%
  ungroup() %>%
  group_by(week, val_diff_bin_str, type) %>%
  summarise(sem_left = sd(mean_left)/sqrt(n()),
            mean_left = mean(mean_left), .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_left, color=type))+
  geom_hline(aes(yintercept=.5), color="gray")+
  geom_vline(aes(xintercept=6), color="gray")+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_left-sem_left, ymax=mean_left+sem_left), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_grid(.~week)+
  labs(x = "Value Left - Value Right", y = "p(Left)", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("","-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225",""))+
  scale_y_continuous(breaks = seq(0,1,.5))

p
# ggsave(file=paste0(fig_out_path, 'bc_group_pLeftByValDiff.jpg'), p, height = 3, width=9, units="in")
```

```{r}
p = data_bc_clean %>%
  filter(abs(val_diff_bin) != 6) %>%
  group_by(subnum, day, val_diff_bin_str, type) %>%
  summarise(mean_left = mean(leftChosen),.groups="keep") %>%
  ungroup() %>%
  group_by(day, val_diff_bin_str, type) %>%
  summarise(sem_left = sd(mean_left)/sqrt(n()),
            mean_left = mean(mean_left), .groups="keep") %>%
    mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 2", "Day 3", "Day 4", "Day 5", "Day 6", "Day 7", "Day 8", "Day 9", "Day 10", "Day 11"))) %>%
  ggplot(aes(val_diff_bin_str, mean_left, color=type))+
  geom_hline(aes(yintercept=.5), color="gray")+
  geom_vline(aes(xintercept=6), color="gray")+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_left-sem_left, ymax=mean_left+sem_left), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_wrap(~day)+
  labs(x = "Value Left - Value Right", y = "p(Left)", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("","-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225",""))+
  scale_y_continuous(breaks = seq(0,1,.5))

p
# ggsave(file=paste0(fig_out_path, 'bc_group_pLeftByValDiffByDay.jpg'), p, height = 6, width = 10, units="in")
```

```{r}
p = data_bc_clean %>%
  filter(abs(val_diff_bin) != 6) %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_left = mean(leftChosen),
            sem_left = sd(leftChosen)/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_left, color=type))+
  # geom_point()+
  geom_jitter(width=.2)+
  geom_errorbar(aes(ymin=mean_left-sem_left, ymax=mean_left+sem_left), width=0)+
  geom_line(aes(group=type))+
  facet_grid(subnum~week)+
  geom_hline(aes(yintercept=.5), color="gray", linetype = "longdash")+
  geom_vline(aes(xintercept=6), color="gray", linetype = "longdash")+
  labs(x = "Value Left - Value Right", y = "p(Left)", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("","-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225",""))+
  scale_y_continuous(breaks = seq(0,1,.5))

p
# ggsave(file=paste0(fig_out_path, 'bc_pLeftByValDiff.jpg'), p, height = 7, width=8, units="in")
```

```{r}
p = data_bc_clean %>%
  filter(abs(val_diff_bin) != 6) %>%
  filter(fmri==1) %>%
  group_by(subnum, day, val_diff_bin_str, type) %>%
  summarise(mean_left = mean(leftChosen),
            sem_left = sd(leftChosen)/sqrt(n()),
            .groups="keep") %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels  = c("Day 3", "Day 7", "Day 11"))) %>%
  ggplot(aes(val_diff_bin_str, mean_left, color=type))+
  # geom_point()+
  geom_jitter(width=.2)+
  geom_errorbar(aes(ymin=mean_left-sem_left, ymax=mean_left+sem_left), width=0)+
  geom_line(aes(group=type))+
  facet_grid(subnum~day)+
  geom_hline(aes(yintercept=.5), color="gray", linetype = "longdash")+
  geom_vline(aes(xintercept=6), color="gray", linetype = "longdash")+
  labs(x = "Value Left - Value Right", y = "p(Left)", title="BC Task (fMRI sessions)", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("","-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225",""))+
  scale_y_continuous(breaks = seq(0,1,.5))

p
# ggsave(file=paste0(fig_out_path, 'bc_pLeftByValDiffMRI.jpg'), p, height = 7, width=8, units="in")
```

# RT over days

## YN Task

```{r}
p = data_yn_clean %>%
  group_by(subnum, day, type) %>%
  summarise(mean_log_rt = mean(log(rt)), .groups="keep") %>%
  ungroup() %>%
  group_by(day, type) %>%
  summarise(.groups = "keep",
            sem_log_rt = sd(mean_log_rt)/sqrt(n()),
            mean_log_rt = mean(mean_log_rt)) %>%
  ggplot(aes(day, mean_log_rt, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0, size = 1)+
  geom_line()+
  # facet_wrap(~subnum)+
  labs(x = "Day", y = "Mean Log RT", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks=seq(1,11,1))+
  scale_color_brewer(palette = "Dark2")

p
# ggsave(file=paste0(fig_out_path, 'yn_group_RTOverDays.jpg'), p, height = 3, width = 5, units="in")
```

```{r}
p = data_yn_clean %>%
  group_by(subnum, day, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            sem_log_rt = sd(log(rt))/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(day, mean_log_rt, color=type))+
  geom_point()+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0)+
  geom_line()+
  facet_wrap(~subnum)+
  labs(x = "Day", y = "Mean Log RT", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks=seq(1,11,1))+
  scale_color_brewer(palette = "Dark2")

p
# ggsave(file=paste0(fig_out_path, 'yn_RTOverDays.jpg'), p, height = 5, width=8, units="in")
```

## BC Task

```{r}
p = data_bc_clean %>%
  group_by(subnum, day, type) %>%
  summarise(mean_log_rt = mean(log(rt)),.groups="keep") %>%
  ungroup() %>%
  group_by(day, type) %>%
  summarise(sem_log_rt = sd(mean_log_rt)/sqrt(n()),
            mean_log_rt = mean(mean_log_rt), .groups="keep") %>%
  ggplot(aes(day, mean_log_rt, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0, size = 1)+
  geom_line()+
  labs(x = "Day", y = "Mean Log RT", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks=seq(1,11,1))+
  scale_color_brewer(palette = "Dark2")

p
# ggsave(file=paste0(fig_out_path, 'bc_group_RTOverDays.jpg'), p, height = 3, width = 5, units="in")
```

```{r}
p = data_bc_clean %>%
  group_by(subnum, day, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            sem_log_rt = sd(log(rt))/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(day, mean_log_rt, color=type))+
  geom_point()+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0)+
  geom_line()+
  facet_wrap(~subnum)+
  labs(x = "Day", y = "Mean Log RT", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks=seq(1,11,1))+
  scale_color_brewer(palette = "Dark2")

p
# ggsave(file=paste0(fig_out_path, 'bc_RTOverDays.jpg'), p, height = 5, width=8, units="in")
```

# RT depending on value difference

## YN Task

```{r}
p = data_yn_clean %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            .groups="keep") %>%
  ungroup() %>%
  group_by(week, val_diff_bin_str, type) %>%
  summarise(sem_log_rt = sd(mean_log_rt)/sqrt(n()),
            mean_log_rt = mean(mean_log_rt), .groups = "keep") %>%
  ggplot(aes(val_diff_bin_str, mean_log_rt, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_grid(.~week)+
  labs(x = "Value Stim - Value Reference", y = "Mean Log RT", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(-1,.5,.5))

p
# ggsave(file=paste0(fig_out_path, 'yn_group_RTOverValDiff.jpg'), p, height = 3, width=9, units="in")
```

```{r}
p = data_yn_clean %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            sem_log_rt = sd(log(rt))/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_log_rt, color=type))+
  # geom_point()+
  geom_jitter(width=.2)+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0)+
  geom_line(aes(group=type))+
  facet_grid(subnum~week)+
  labs(x = "Value Stim - Value Reference", y = "Mean Log RT", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(-1,.5,.5))

p
# ggsave(file=paste0(fig_out_path, 'yn_RTOverValDiff.jpg'), p, height = 5, width=8, units="in")
```

## BC Task

```{r}
p = data_bc_clean %>%
  filter(abs(val_diff_bin) != 6) %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            .groups="keep") %>%
  ungroup() %>%
  group_by(week, val_diff_bin_str, type) %>%
  summarise(sem_log_rt = sd(mean_log_rt)/sqrt(n()),
            mean_log_rt = mean(mean_log_rt), .groups = "keep") %>%
  ggplot(aes(val_diff_bin_str, mean_log_rt, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_grid(.~week)+
  labs(x = "Value Left - Value Right", y = "Mean Log RT", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("","-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225",""))+
  scale_y_continuous(breaks = seq(-1,.5,.5))

p
# ggsave(file=paste0(fig_out_path, 'bc_group_RTOverValDiff.jpg'), p, height = 3, width=9, units="in")
```

```{r}
p = data_bc_clean %>%
  filter(abs(val_diff_bin) != 6) %>%
  group_by(subnum, week, val_diff_bin_str, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            sem_log_rt = sd(log(rt))/sqrt(n()),
            .groups="keep") %>%
  ggplot(aes(val_diff_bin_str, mean_log_rt, color=type))+
  geom_point()+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0)+
  geom_line(aes(group=type))+
  facet_grid(subnum~week)+
  labs(x = "Value Left - Value Right", y = "Mean Log RT", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_x_discrete(labels=c("","-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225",""))+
  scale_y_continuous(breaks = seq(-1,.5,.5))

p
# ggsave(file=paste0(fig_out_path, 'bc_RTOverValDiff.jpg'), p, height = 5, width=8, units="in")
```

# Fixation Cross Free RT

What does the distribution of free RTs during the fixation look like?

## YN Task

For task_beah (non-fmri sessions) `startFix` is when the fixation comes on

```{r}
yn_fix_rt_data = data_yn_clean %>%
  filter(fmri == 0) %>%
  select(-evtimeON, -evtimeOFF, -fmri, -response, -valueO, -valueF, -valueS, -stimNum, -crossON) %>%
  group_by(subnum, day, session) %>%
  mutate(trialNum = 1:n(),
         startFixDiff = c(diff(startFix), NA), 
         rewardTime = ifelse(session == 1 & trialNum < 16, 2.4, ifelse(session == 1 & trialNum > 15 & trialNum < 36, 1.5, 1))) %>%
  filter(!is.na(startFixDiff)) %>%
  mutate(fixRt = startFixDiff - (rt+rewardTime))
```

There are some very long RTs during the fixation cross

```{r}
summary(yn_fix_rt_data$fixRt)
```

But less than 2% of all trials have fixations RTs slower than 1 second.

```{r}
sum(yn_fix_rt_data$fixRt>1)/nrow(yn_fix_rt_data)
```

Excluding slow fixation RTs for the plot

```{r}
yn_fix_rt_data %>%
  filter(fixRt < 1) %>%
  ggplot(aes(fixRt))+
  geom_histogram(alpha=.5, bins=30)+
  facet_wrap(~subnum)+
  theme(panel.grid = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())+
  labs(y="", x = "Fixation Cross RT", title = "Y/N Task")

```

```{r}
p = yn_fix_rt_data %>%
  filter(fixRt < 1) %>%
  ungroup() %>%
  group_by(subnum, day) %>%
  summarise(.groups="keep",
            mean_log_fix_rt = mean(log(fixRt)),
            sem_log_fix_rt = sd(log(fixRt))/sqrt(n())) %>%
  mutate(subnum = as.factor(subnum)) %>%
  ggplot(aes(day, mean_log_fix_rt, color=subnum))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_log_fix_rt - sem_log_fix_rt, ymax = mean_log_fix_rt + sem_log_fix_rt), width= 0, size=1)+
  geom_line()+
  labs(x="Day", y = "Mean Log Fixation Cross RT", title = "Y/N Task")+
  scale_x_continuous(breaks=seq(1,11,1))+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")

p
# ggsave(file=paste0(fig_out_path, 'yn_fixRTOverDays.jpg'), p, height = 3, width=5, units="in")
```

## BC Task

```{r}
bc_fix_rt_data = data_bc_clean %>%
  filter(fmri == 0) %>%
  select(subnum, day, rt, startFix) %>%
  group_by(subnum, day) %>%
  mutate(trialNum = 1:n(),
         startFixDiff = c(diff(startFix), NA), 
         rewardTime = 1.1) %>%
  filter(!is.na(startFixDiff)) %>%
  mutate(fixRt = startFixDiff - (rt+rewardTime))
```

```{r}
summary(bc_fix_rt_data$fixRt)
```

But less than 2% of all trials have fixations RTs slower than 1 second.

```{r}
sum(bc_fix_rt_data$fixRt>1)/nrow(bc_fix_rt_data)
```

Excluding slow fixation RTs for the plot

```{r}
bc_fix_rt_data %>%
  filter(fixRt < 1) %>%
  ggplot(aes(fixRt))+
  geom_histogram(alpha=.5, bins=30)+
  facet_wrap(~subnum)+
  theme(panel.grid = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())+
  labs(y="", x = "Fixation Cross RT", title = "BC Task")

```

```{r}
p = bc_fix_rt_data %>%
  filter(fixRt < 1) %>%
  ungroup() %>%
  group_by(subnum, day) %>%
  summarise(.groups="keep",
            mean_log_fix_rt = mean(log(fixRt)),
            sem_log_fix_rt = sd(log(fixRt))/sqrt(n())) %>%
  mutate(subnum = as.factor(subnum)) %>%
  ggplot(aes(day, mean_log_fix_rt, color=subnum))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_log_fix_rt - sem_log_fix_rt, ymax = mean_log_fix_rt + sem_log_fix_rt), width= 0, size = 1)+
  geom_line()+
  theme(panel.grid = element_blank())+
  labs(x="Day", y = "Mean Log Fixation Cross RT", title = "BC Task")+
  scale_x_continuous(breaks=seq(1,11,1))+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")

p
# ggsave(file=paste0(fig_out_path, 'bc_fixRTOverDays.jpg'), p, height = 3, width=5, units="in")

```



