---
title: "Novel vs. repeated choice project: Understanding how fillings are created for experimental stimuli"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

```{r include=FALSE}
library(tidyverse)
library(here)
theme_set(theme_bw())
helpers_path = paste0(here(),'/analysis/helpers/')
source(paste0(helpers_path, '01_clean_behavioral_data.R'))
```


Matlab code from ... that determines the filling value for each stimulus

```
bothCol = [0.1 0.1 0.4 -99;
            0.4 0.1 0.1 -99]; 

if  mydata.filling(indextrial)>=0
    colorStim = bothCol(1,:);
    switch  abs(mydata.filling(indextrial))
        case 0.4
            colorStim(3)= 0.6;
        case 0.6
            colorStim(3)= 0.5;
        case 0.85
            colorStim(3)= 0.3;
    end   
else
    colorStim = bothCol(2,:);
    switch  abs(mydata.filling(indextrial))
        case 0.4
            colorStim(1)= 0.6;
        case 0.6
            colorStim(1)= 0.5;
        case 0.85
            colorStim(1)= 0.3;
    end
end
colorStim(4)=abs(mydata.filling(indextrial));
```

```{r}
unique(data_yn_clean$filling)
```

```{r}
convertFVToHEX = function(fillingVal){
  
  bothCol = matrix(data = c(.1 , .1, .4, -99, .4, .1, .1, -99), byrow=T, nrow=2, ncol=4)
  
  if(fillingVal>=0){
    colorStim = bothCol[1,]
    colorStim[3] = ifelse(abs(fillingVal)==.4, .6, ifelse(abs(fillingVal)==.6,.5, ifelse(abs(fillingVal)==.85, .3, colorStim[3])))
    
  } else{
    colorStim = bothCol[2,]
    colorStim[1] = ifelse(abs(fillingVal)==.4, .6, ifelse(abs(fillingVal)==.6,.5, ifelse(abs(fillingVal)==.85, .3, colorStim[1])))
  }
  
  colorStim[4] = abs(fillingVal)
  
  hex_code = rgb(colorStim[1], colorStim[2], colorStim[3], colorStim[4])
  

  return(hex_code)
}
```

```{r}
dat = data.frame(filling = unique(data_yn_clean$filling))

for(i in 1:nrow(dat)){
  dat$hex_code[i] = convertFVToHEX(dat$filling[i])
}

dat = dat %>%
  arrange(filling)

dat
```

```{r}
ggplot()+
  annotate("rect", xmin=c(1,2,3,1,2,3,1,2,3), xmax=c(2,3,4,2,3,4,2,3,4), ymin=c(1,1,1,2,2,2,3,3,3) , ymax=c(2,2,2,3,3,3,4,4,4), fill=c(dat$hex_code))+
  annotate("text", x=c(1,2,3,1,2,3,1,2,3)+.5, y=c(1,1,1,2,2,2,3,3,3)+.5 , label=c(dat$filling))+
  theme(axis.ticks = element_blank(),
        axis.text = element_blank(),
        panel.grid = element_blank(),
        axis.title = element_blank(),
        panel.border = element_blank())
```

The stimuli are not gambles. If they are chosen to be played they always yield the same reward. If they are not chosen then they yield the reference amount.

```{r}
tmp = data_yn_clean %>%
  filter(yesChosen == 1) %>%
  select(possiblePayoff, payoff)

sum(tmp$possiblePayoff == tmp$payoff) == nrow(tmp)
```

How many HT and RE trials in each session?

```{r}
with(data_yn_clean, table(type, day, fmri, subnum))
```

```{r}
with(data_bc_clean, table(typeLeft, day, fmri, subnum))
```

3 features: 
Shape 6
Orientation 11
Filling 11

Does the orientation and filling have the same value for each shape?

```{r}
dat = data_yn_clean %>%
  filter(subnum == 601) %>%
  select(subnum, day, stimNum, type, orientation, filling, shape, valueO, valueF, valueS, possiblePayoff)
```

Each shape has one value

```{r}
with(dat, table(shape, valueS))
```
Each orientation has one value

```{r}
with(dat, table(orientation, valueO))
```
One filling level has two values!

```{r}
with(dat, table(filling, valueF))
```
```{r}
with(dat, table(valueO, valueF, shape))
```

% all(:,4) <- shape value
% all(:,5) <- orientation value
% all(:,6) <- filling color value

round(((all(:,4) + all(:,5) + all(:,6))/2)*100)

```{r}
dat %>%
  select(valueO, valueF, valueS, possiblePayoff) %>%
  mutate(guess = round(100 * ((valueS + valueO + valueF)/2) ))
```
