---
title: "Novel vs. repeated choice project: Behavioral Modeling"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Set up environment and load in data

```{r include=FALSE, message=FALSE}
library(tidyverse)
library(brms)
library(here)
theme_set(theme_bw())
helpers_path = paste0(here(),'/analysis/helpers/')
source(paste0(helpers_path, '01_clean_behavioral_data.R'))
fig_out_path = paste0(here(), '/outputs/fig/')
```

Add columns that will be used for plots below.

```{r}
data_yn_clean = data_yn_clean %>%
  mutate(correct = ifelse(possiblePayoff>reference & yesChosen == 1, 1, ifelse(possiblePayoff < reference & yesChosen == 0, 1, 0))) %>%
  mutate(type = ifelse(type == 1, "HT", "RE"),
         week = ifelse(week == 1, "Week 1", ifelse(week == 2, "Week 2", ifelse(week == 3, "Week 3", NA))),
         week = factor(week, levels = c("Week 1", "Week 2", "Week 3"))) %>%
  mutate(val_diff = possiblePayoff - reference,
         val_diff_bin = round(val_diff/50),
         val_diff_bin_str = paste0(val_diff_bin*50-25,":",val_diff_bin*50+25),
         val_diff_bin_str = factor(val_diff_bin_str, levels = c("-225:-175", "-175:-125", "-125:-75", "-75:-25", "-25:25", "25:75", "75:125", "125:175", "175:225")))

data_bc_clean = data_bc_clean %>%
  mutate(correct = ifelse(possiblePayoffleft>possiblePayoffright & leftChosen == 1, 1, ifelse(possiblePayoffleft<possiblePayoffright & leftChosen == 0, 1, 0))) %>%
  mutate(type = ifelse(typeLeft == 1, "HT", "RE"),
         week = ifelse(week == 1, "Week 1", ifelse(week == 2, "Week 2", ifelse(week == 3, "Week 3", NA))),
         week = factor(week, levels = c("Week 1", "Week 2", "Week 3"))) %>%
  mutate(val_diff = possiblePayoffleft - possiblePayoffright,
         val_diff_bin = round(val_diff/50),
         val_diff_bin_str = paste0(val_diff_bin*50-25,":",val_diff_bin*50+25),
         val_diff_bin_str = factor(val_diff_bin_str, levels = c("-275:-225","-225:-175", "-175:-125", "-125:-75", "-75:-25", "-25:25", "25:75", "75:125", "125:175", "175:225", "225:275"))) %>%
  filter(!is.na(val_diff_bin_str))
```

Center variables!

```{r}
data_yn_clean = data_yn_clean %>%
  mutate(day_std = (day - mean(day))/sd(day)) %>%
  group_by(subnum) %>%
  mutate(val_diff_std = (val_diff - mean(val_diff))/sd(val_diff),
         abs_val_diff = abs(val_diff),
         abs_val_diff_std = (abs_val_diff - mean(abs_val_diff))/sd(abs_val_diff))
```

```{r}
data_bc_clean = data_bc_clean %>%
  mutate(day_std = (day - mean(day))/sd(day)) %>%
  group_by(subnum) %>%
  mutate(val_diff_std = (val_diff - mean(val_diff))/sd(val_diff),
         abs_val_diff = abs(val_diff),
         abs_val_diff_std = (abs_val_diff - mean(abs_val_diff))/sd(abs_val_diff))
```

Would you mind looking at the full RT distributions for different value diffs, separately for Y/N and binary choice trials, and for the two type of stimuli? I’m curious to see if there is evidence for some bi-modality for the repeated stimuli (especially after learning), which would suggest that choice is made with a “different fast process” with some probability.

```{r}

```

# Logits for choice in Y/N and BC

## YN task

Does the logit slope change across days? (value_diff:day interaction)  
Is the logit slope different depending on the stim type? (value_diff:type interaction)  
Does it change differently depending on the stim type? (value_diff:day:type interaction)  

Run logits, extract draws and ppc, save output.  

```{r}

fn_draws = paste0(helpers_path, '/inputs/yn_logit_draws.csv')
fn_ppc = paste0(helpers_path, '/inputs/yn_logit_ppc.csv')

if(file.exists(fn_draws) & file.exists(fn_ppc)){
  yn_logit_draws = read.csv(fn_draws)
  yn_logit_ppc = read.csv(fn_ppc)
} else{
  subnums = unique(data_yn_clean$subnum)
  
  yn_logit_draws = data_frame()
  yn_logit_ppc = data_frame()
  
  for(i in 1:length(subnums)){
    cur_sub = subnums[i]
    
    cur_yn_data = data_yn_clean %>% 
      ungroup() %>%
      filter(subnum == cur_sub) %>%
      select(val_diff_bin_str, val_diff_std, day_std, type, val_diff, day, yesChosen)
    
    
    cur_yn_logit <- brm(formula = yesChosen ~ val_diff_std * day_std * type,
                        data= cur_yn_data,
                        family = bernoulli(link = "logit"),
                        warmup = 500,
                        iter = 2500,
                        chains = 4,
                        init = "0",
                        cores = 4,
                        seed = 389253)
    
    cur_draws = as_draws_df(cur_yn_logit)
    cur_draws$subnum = cur_sub
    
    yn_logit_draws = rbind(yn_logit_draws, cur_draws)
    
    cur_pred = fitted(cur_yn_logit, newdata = cur_yn_data %>%
                        select(-val_diff, -day, -yesChosen, -val_diff_bin_str), scale = "linear") %>%
      as_tibble() %>%
      transmute(prob = Estimate %>% inv_logit_scaled()) %>%
      bind_cols(cur_yn_data) %>%
      mutate(subnum = cur_sub)
    
    yn_logit_ppc = rbind(yn_logit_ppc, cur_pred)
  }
  names(yn_logit_draws) = gsub(":", ".", names(yn_logit_draws))
  write.csv(yn_logit_draws, fn_draws, row.names = F)
  write.csv(yn_logit_ppc, fn_ppc, row.names = F)
  
  rm(cur_yn_data, cur_yn_logit, cur_draws, cur_pred)
}

```

Examine chains for the three variables of interest  

```{r}
as.data.frame(yn_logit_draws) %>%
  select("b_val_diff_std.day_std", "b_val_diff_std.typeRE", "b_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  ggplot(aes(.iteration, value, color = as.factor(.chain)))+
  geom_line()+
  facet_grid(subnum ~ key, scales = 'free_y')+
  labs(x = "", y = "") +
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
  
```

Examine autocorrelation in the variables of interest.  

```{r}
as.data.frame(yn_logit_draws) %>%
  select("b_val_diff_std.day_std", "b_val_diff_std.typeRE", "b_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  group_by(subnum, .chain, key) %>%
  summarise(lag0 = acf(value, lag.max=1, plot = F)[["acf"]][1],
            lag1 = acf(value, lag.max=1, plot = F)[["acf"]][2],
            lag2 = acf(value, lag.max=2, plot = F)[["acf"]][3],
            lag3 = acf(value, lag.max=3, plot = F)[["acf"]][4],
            lag4 = acf(value, lag.max=4, plot = F)[["acf"]][5],
            lag5 = acf(value, lag.max=5, plot = F)[["acf"]][6],
            lag6 = acf(value, lag.max=6, plot = F)[["acf"]][7],
            lag7 = acf(value, lag.max=7, plot = F)[["acf"]][8],
            lag8 = acf(value, lag.max=8, plot = F)[["acf"]][9],
            lag9 = acf(value, lag.max=9, plot = F)[["acf"]][10],
            lag10 = acf(value, lag.max=10, plot = F)[["acf"]][11],
            lag11 = acf(value, lag.max=11, plot = F)[["acf"]][12], .groups = 'keep') %>%
  gather(lag, cor, -subnum, -.chain, -key) %>%
  mutate(lag = gsub("lag", "", lag),
         lag = as.numeric(lag)) %>%
  ggplot(aes(lag, cor, fill = as.factor(.chain)))+
  geom_bar(stat = "identity", alpha=.5, position = "identity", color = NA)+
  facet_grid(subnum ~ key)+
  labs(x = "Lag", y = "Correlation") +
  theme(legend.position = "none",
        panel.grid = element_blank())+
  scale_x_continuous(breaks = c(0, 5, 10))+
  scale_y_continuous(breaks = c(0, .5, 1))
```

Examine parameter distributions  
Parameter distributions collapsed across subjects (similar to a random slopes analysis)

```{r}
p = as.data.frame(yn_logit_draws) %>%
  select("b_val_diff_std.day_std", "b_val_diff_std.typeRE", "b_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  mutate(key = ifelse(key == "b_val_diff_std.day_std", "Value Diff * Day", ifelse(key == "b_val_diff_std.typeRE", "Value Diff * Type", ifelse(key == "b_val_diff_std.day_std.typeRE", "Value Diff * Day * Type", NA))),
         key = factor(key, levels = c("Value Diff * Type", "Value Diff * Day", "Value Diff * Day * Type"))) %>%
  ggplot(aes(value)) +
  geom_density(aes(fill = as.factor(subnum)), position="identity", alpha=.75, color=NA) +
  geom_vline(aes(xintercept = 0), color = "light gray") + 
  facet_wrap(~key) +
  labs(x = "Parameter Estimate", y = "", fill = "Subject") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks = c(0)) +
  guides(fill=guide_legend(nrow=1))

p
# ggsave(file=paste0(fig_out_path, 'yn_logit_interactionParEsts.jpg'), p, height = 3, width = 9, units="in")
```

Interpreting the three way interaction: Is the valDiff * Day interaction smaller for type == RE?

```{r}
m1 = brm(formula = yesChosen ~ val_diff_std * day_std,
                        data= data_yn_clean %>% filter(subnum == 601 & type == "RE"),
                        family = bernoulli(link = "logit"),
                        warmup = 500,
                        iter = 2500,
                        chains = 4,
                        init = "0",
                        cores = 4,
                        seed = 389253)

m2 = brm(formula = yesChosen ~ val_diff_std * day_std,
                        data= data_yn_clean %>% filter(subnum == 601 & type == "HT"),
                        family = bernoulli(link = "logit"),
                        warmup = 500,
                        iter = 2500,
                        chains = 4,
                        init = "0",
                        cores = 4,
                        seed = 389253)
```

```{r}
summary(m1)
```

```{r}
summary(m2)
```

**Plot predicted plots on top of observed data**

```{r}
yn_data_summary = data_yn_clean %>%
  mutate(val_diff_bin_midpoint = round(val_diff/50)*50) %>%
  group_by(subnum, day, val_diff_bin_str, type) %>%
  summarise(sem_yes = sd(yesChosen)/sqrt(n()),
            mean_yes = mean(yesChosen), 
            val_diff = unique(val_diff_bin_midpoint),.groups="keep") %>%
  filter(day %in% c(1, 3, 7, 11)) %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 3", "Day 7", "Day 11")))
  


p = yn_logit_ppc %>% 
  filter(day %in% c(1, 3, 7, 11)) %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 3", "Day 7", "Day 11"))) %>%
  ggplot()+
  geom_vline(aes(xintercept = 0), color = "light gray")+
  geom_hline(aes(yintercept = 0.5), color = "light gray")+
  geom_line(aes(x = val_diff, y = prob, color=type))+
  geom_point(data = yn_data_summary, aes(x = val_diff, y = mean_yes, color = type)) +
  geom_errorbar(data = yn_data_summary, aes(x = val_diff, y = mean_yes, ymin = mean_yes - sem_yes, ymax = mean_yes + sem_yes, color= type), width = 0) +
  facet_grid(subnum~day) + 
  labs(x = "Value Stim - Value Reference", y = "p(Yes)", title="Y/N Task - True vs Predicted", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_y_continuous(breaks = seq(0,1,.5))

# ggsave(file=paste0(fig_out_path, 'yn_logit_ppc.jpg'), p, height = 6, width = 10, units="in")
p
```

## BC task

```{r}
fn_draws = paste0(helpers_path, '/inputs/bc_logit_draws.csv')
fn_ppc = paste0(helpers_path, '/inputs/bc_logit_ppc.csv')

if(file.exists(fn_draws) & file.exists(fn_ppc)){
  bc_logit_draws = read.csv(fn_draws)
  bc_logit_ppc = read.csv(fn_ppc)
} else{
  subnums = unique(data_bc_clean$subnum)
  
  bc_logit_draws = data_frame()
  bc_logit_ppc = data_frame()
  
  for(i in 1:length(subnums)){
    cur_sub = subnums[i]
    
    cur_bc_data = data_bc_clean %>% 
      ungroup() %>%
      filter(subnum == cur_sub) %>%
      select(val_diff_bin_str, val_diff_std, day_std, type, val_diff, day, leftChosen)
    
    
    cur_bc_logit <- brm(formula = leftChosen ~ val_diff_std * day_std * type,
                        data= cur_bc_data,
                        family = bernoulli(link = "logit"),
                        warmup = 500,
                        iter = 2500,
                        chains = 4,
                        init = "0",
                        cores = 4,
                        seed = 389253)
    
    cur_draws = as_draws_df(cur_bc_logit)
    cur_draws$subnum = cur_sub
    
    bc_logit_draws = rbind(bc_logit_draws, cur_draws)
    
    cur_pred = fitted(cur_bc_logit, newdata = cur_bc_data %>%
                        select(-val_diff, -day, -leftChosen, -val_diff_bin_str), scale = "linear") %>%
      as_tibble() %>%
      transmute(prob = Estimate %>% inv_logit_scaled()) %>%
      bind_cols(cur_bc_data) %>%
      mutate(subnum = cur_sub)
    
    bc_logit_ppc = rbind(bc_logit_ppc, cur_pred)
  }
  names(bc_logit_draws) = gsub(":", ".", names(bc_logit_draws))
  write.csv(bc_logit_draws, fn_draws, row.names = F)
  write.csv(bc_logit_ppc, fn_ppc, row.names = F)
  
  rm(cur_bc_data, cur_bc_logit, cur_draws, cur_pred)
}

```

Examine chains for the three variables of interest  

```{r}
as.data.frame(bc_logit_draws) %>%
  select("b_val_diff_std.day_std", "b_val_diff_std.typeRE", "b_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  ggplot(aes(.iteration, value, color = as.factor(.chain)))+
  geom_line()+
  facet_grid(subnum ~ key, scales = 'free_y')+
  labs(x = "", y = "") +
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
  
```

Examine autocorrelation in the variables of interest.  

```{r}
as.data.frame(bc_logit_draws) %>%
  select("b_val_diff_std.day_std", "b_val_diff_std.typeRE", "b_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  group_by(subnum, .chain, key) %>%
  summarise(lag0 = acf(value, lag.max=1, plot = F)[["acf"]][1],
            lag1 = acf(value, lag.max=1, plot = F)[["acf"]][2],
            lag2 = acf(value, lag.max=2, plot = F)[["acf"]][3],
            lag3 = acf(value, lag.max=3, plot = F)[["acf"]][4],
            lag4 = acf(value, lag.max=4, plot = F)[["acf"]][5],
            lag5 = acf(value, lag.max=5, plot = F)[["acf"]][6],
            lag6 = acf(value, lag.max=6, plot = F)[["acf"]][7],
            lag7 = acf(value, lag.max=7, plot = F)[["acf"]][8],
            lag8 = acf(value, lag.max=8, plot = F)[["acf"]][9],
            lag9 = acf(value, lag.max=9, plot = F)[["acf"]][10],
            lag10 = acf(value, lag.max=10, plot = F)[["acf"]][11],
            lag11 = acf(value, lag.max=11, plot = F)[["acf"]][12], .groups = 'keep') %>%
  gather(lag, cor, -subnum, -.chain, -key) %>%
  mutate(lag = gsub("lag", "", lag),
         lag = as.numeric(lag)) %>%
  ggplot(aes(lag, cor, fill = as.factor(.chain)))+
  geom_bar(stat = "identity", alpha=.5, position = "identity", color = NA)+
  facet_grid(subnum ~ key)+
  labs(x = "Lag", y = "Correlation") +
  theme(legend.position = "none",
        panel.grid = element_blank())+
  scale_x_continuous(breaks = c(0, 5, 10))+
  scale_y_continuous(breaks = c(0, .5, 1))
```

Examine parameter distributions

```{r}
p = as.data.frame(bc_logit_draws) %>%
  select("b_val_diff_std.day_std", "b_val_diff_std.typeRE", "b_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  mutate(key = ifelse(key == "b_val_diff_std.day_std", "Value Diff * Day", ifelse(key == "b_val_diff_std.typeRE", "Value Diff * Type", ifelse(key == "b_val_diff_std.day_std.typeRE", "Value Diff * Day * Type", NA))),
         key = factor(key, levels = c("Value Diff * Type", "Value Diff * Day", "Value Diff * Day * Type"))) %>%
  ggplot(aes(value, fill = as.factor(subnum))) +
  geom_density(position="identity", alpha=.75, color=NA) +
  geom_vline(aes(xintercept = 0), color = "light gray") + 
  facet_wrap(~key) +
  labs(x = "Parameter Estimate", y = "", fill = "Subject") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks = c(0)) +
  guides(fill=guide_legend(nrow=1))

p
# ggsave(file=paste0(fig_out_path, 'bc_logit_interactionParEsts.jpg'), p, height = 3, width = 9, units="in")
```


**Plot predicted plots on top of observed data**

```{r}
bc_data_summary = data_bc_clean %>%
  mutate(val_diff_bin_midpoint = round(val_diff/50)*50) %>%
  group_by(subnum, day, val_diff_bin_str, type) %>%
  summarise(sem_left = sd(leftChosen)/sqrt(n()),
            mean_left = mean(leftChosen), 
            val_diff = unique(val_diff_bin_midpoint),.groups="keep") %>%
  filter(day %in% c(1, 3, 7, 11)) %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 3", "Day 7", "Day 11")))
  


p = bc_logit_ppc %>% 
  filter(day %in% c(1, 3, 7, 11)) %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 3", "Day 7", "Day 11"))) %>%
  ggplot()+
  geom_vline(aes(xintercept = 0), color = "light gray")+
  geom_hline(aes(yintercept = 0.5), color = "light gray")+
  geom_line(aes(x = val_diff, y = prob, color=type))+
  geom_point(data = bc_data_summary, aes(x = val_diff, y = mean_left, color = type)) +
  geom_errorbar(data = bc_data_summary, aes(x = val_diff, y = mean_left, ymin = mean_left - sem_left, ymax = mean_left + sem_left, color= type), width = 0) +
  facet_grid(subnum~day) + 
  labs(x = "Value Left - Value Right", y = "p(Left)", title="BC Task - True vs Predicted", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  scale_y_continuous(breaks = seq(0,1,.5))

# ggsave(file=paste0(fig_out_path, 'bc_logit_ppc.jpg'), p, height = 6, width = 10, units="in")
p
```

# RT slope 

```{r}
data_yn_clean = data_yn_clean %>%
  mutate(log_rt = log(rt))

data_bc_clean = data_bc_clean %>%
  mutate(log_rt = log(rt))
```

## YN task

```{r}

fn_draws = paste0(helpers_path, '/inputs/yn_rt_draws.csv')
fn_ppc = paste0(helpers_path, '/inputs/yn_rt_ppc.csv')

if(file.exists(fn_draws) & file.exists(fn_ppc)){
  yn_rt_draws = read.csv(fn_draws)
  yn_rt_ppc = read.csv(fn_ppc)
} else{
  subnums = unique(data_yn_clean$subnum)
  
  yn_rt_draws = data_frame()
  yn_rt_ppc = data_frame()
  
  for(i in 1:length(subnums)){
    cur_sub = subnums[i]
    
    cur_yn_data = data_yn_clean %>% 
      ungroup() %>%
      filter(subnum == cur_sub) %>%
      select(abs_val_diff_std, day_std, type, abs_val_diff, day, log_rt)
    
    
    cur_yn_rt <- brm(formula = log_rt ~ abs_val_diff_std * day_std * type,
                        data= cur_yn_data,
                        warmup = 500,
                        iter = 2500,
                        chains = 4,
                        init = "0",
                        cores = 4,
                        seed = 389253)
    
    cur_draws = as_draws_df(cur_yn_rt)
    cur_draws$subnum = cur_sub
    
    yn_rt_draws = rbind(yn_rt_draws, cur_draws)
    
    cur_pred = fitted(cur_yn_rt, newdata = cur_yn_data %>%
                        select(-abs_val_diff, -day, -log_rt)) %>% 
      as_tibble() %>%
      transmute(pred_log_rt = Estimate) %>% #same as mean brms::posterior_epred values not brms::posterior_predict
      bind_cols(cur_yn_data) %>%
      mutate(subnum = cur_sub)
    
    yn_rt_ppc = rbind(yn_rt_ppc, cur_pred)
  }
  names(yn_rt_draws) = gsub(":", ".", names(yn_rt_draws))
  write.csv(yn_rt_draws, fn_draws, row.names = F)
  write.csv(yn_rt_ppc, fn_ppc, row.names = F)
  
  rm(cur_yn_data, cur_yn_rt, cur_draws, cur_pred)
}

```

Examine chains for the three variables of interest  

```{r}
as.data.frame(yn_rt_draws) %>%
  select("b_abs_val_diff_std.day_std", "b_abs_val_diff_std.typeRE", "b_abs_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  ggplot(aes(.iteration, value, color = as.factor(.chain)))+
  geom_line()+
  facet_grid(subnum ~ key, scales = 'free_y')+
  labs(x = "", y = "") +
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
  
```

Examine autocorrelation in the variables of interest.  

```{r}
as.data.frame(yn_rt_draws) %>%
  select("b_abs_val_diff_std.day_std", "b_abs_val_diff_std.typeRE", "b_abs_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  group_by(subnum, .chain, key) %>%
  summarise(lag0 = acf(value, lag.max=1, plot = F)[["acf"]][1],
            lag1 = acf(value, lag.max=1, plot = F)[["acf"]][2],
            lag2 = acf(value, lag.max=2, plot = F)[["acf"]][3],
            lag3 = acf(value, lag.max=3, plot = F)[["acf"]][4],
            lag4 = acf(value, lag.max=4, plot = F)[["acf"]][5],
            lag5 = acf(value, lag.max=5, plot = F)[["acf"]][6],
            lag6 = acf(value, lag.max=6, plot = F)[["acf"]][7],
            lag7 = acf(value, lag.max=7, plot = F)[["acf"]][8],
            lag8 = acf(value, lag.max=8, plot = F)[["acf"]][9],
            lag9 = acf(value, lag.max=9, plot = F)[["acf"]][10],
            lag10 = acf(value, lag.max=10, plot = F)[["acf"]][11],
            lag11 = acf(value, lag.max=11, plot = F)[["acf"]][12], .groups = 'keep') %>%
  gather(lag, cor, -subnum, -.chain, -key) %>%
  mutate(lag = gsub("lag", "", lag),
         lag = as.numeric(lag)) %>%
  ggplot(aes(lag, cor, fill = as.factor(.chain)))+
  geom_bar(stat = "identity", alpha=.5, position = "identity", color = NA)+
  facet_grid(subnum ~ key)+
  labs(x = "Lag", y = "Correlation") +
  theme(legend.position = "none",
        panel.grid = element_blank())+
  scale_x_continuous(breaks = c(0, 5, 10))+
  scale_y_continuous(breaks = c(0, .5, 1))
```

```{r}
p = as.data.frame(yn_rt_draws) %>%
  select("b_abs_val_diff_std.day_std", "b_abs_val_diff_std.typeRE", "b_abs_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  mutate(key = ifelse(key == "b_abs_val_diff_std.day_std", "|Value Diff| * Day", ifelse(key == "b_abs_val_diff_std.typeRE", "|Value Diff| * Type", ifelse(key == "b_abs_val_diff_std.day_std.typeRE", "|Value Diff| * Day * Type", NA))),
         key = factor(key, levels = c("|Value Diff| * Type", "|Value Diff| * Day", "|Value Diff| * Day * Type"))) %>%
  ggplot(aes(value, fill = as.factor(subnum))) +
  geom_density(position="identity", alpha=.75, color=NA) +
  geom_vline(aes(xintercept = 0), color = "light gray") + 
  facet_wrap(~key) +
  # facet_grid(subnum~key) +
  labs(x = "Parameter Estimate", y = "", fill = "Subject") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks = c(0)) +
  guides(fill=guide_legend(nrow=1))

p
# ggsave(file=paste0(fig_out_path, 'yn_rt_interactionParEsts.jpg'), p, height = 3, width = 9, units="in")
```

```{r}
p = data_yn_clean %>%
  mutate(abs_val_diff_bin_str =  paste0(abs(val_diff_bin)*50-25,":",abs(val_diff_bin)*50+25),
         abs_val_diff_bin_str = ifelse(abs_val_diff_bin_str ==  "-25:25", "0:25", abs_val_diff_bin_str),
         abs_val_diff_bin_str = factor(abs_val_diff_bin_str, levels = c("0:25", "25:75", "75:125", "125:175", "175:225", "225:275"))) %>%
  group_by(subnum, week, abs_val_diff_bin_str, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            .groups="keep") %>%
  ungroup() %>%
  group_by(week, abs_val_diff_bin_str, type) %>%
  summarise(sem_log_rt = sd(mean_log_rt)/sqrt(n()),
            mean_log_rt = mean(mean_log_rt), .groups = "keep") %>%
  ggplot(aes(abs_val_diff_bin_str, mean_log_rt, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_grid(.~week)+
  labs(x = "|Value Stim - Value Reference|", y = "Mean Log RT", title="Y/N Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  # scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(-1,.5,.5))

p
# ggsave(file=paste0(fig_out_path, 'yn_group_RTOverAbsValDiff.jpg'), p, height = 3, width=9, units="in")
```

Plot predicted over true

```{r}
yn_data_summary = data_yn_clean %>%
  mutate(abs_val_diff_bin_str =  paste0(abs(val_diff_bin)*50-25,":",abs(val_diff_bin)*50+25),
         abs_val_diff_bin_str = ifelse(abs_val_diff_bin_str ==  "-25:25", "0:25", abs_val_diff_bin_str),
         abs_val_diff_bin_str = factor(abs_val_diff_bin_str, levels = c("0:25", "25:75", "75:125", "125:175", "175:225", "225:275")),
         abs_val_diff_bin_midpoint = round(abs(val_diff)/50)*50) %>%
  group_by(subnum, day, abs_val_diff_bin_str, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            sem_log_rt = sd(log(rt))/sqrt(n()),
            abs_val_diff = unique(abs_val_diff_bin_midpoint),
            .groups="keep") %>%
  filter(day %in% c(1, 3, 7, 11)) %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 3", "Day 7", "Day 11")))

p = yn_rt_ppc %>% 
  filter(day %in% c(1, 3, 7, 11)) %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 3", "Day 7", "Day 11"))) %>%
  ggplot()+
  geom_line(aes(x = abs_val_diff, y = pred_log_rt, color=type))+
  geom_point(data = yn_data_summary, aes(x = abs_val_diff, y = mean_log_rt, color = type)) +
  geom_errorbar(data = yn_data_summary, aes(x = abs_val_diff, y = mean_log_rt, ymin = mean_log_rt - sem_log_rt, ymax = mean_log_rt + sem_log_rt, color= type), width = 0) +
  facet_grid(subnum~day) + 
  labs(x = "|Value Stim - Value Reference|", y = "Log RT", title="Y/N Task - True vs Predicted", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")

# ggsave(file=paste0(fig_out_path, 'yn_rt_ppc.jpg'), p, height = 6, width = 10, units="in")
p
```

## BC task

```{r}

fn_draws = paste0(helpers_path, '/inputs/bc_rt_draws.csv')
fn_ppc = paste0(helpers_path, '/inputs/bc_rt_ppc.csv')

if(file.exists(fn_draws) & file.exists(fn_ppc)){
  bc_rt_draws = read.csv(fn_draws)
  bc_rt_ppc = read.csv(fn_ppc)
} else{
  subnums = unique(data_bc_clean$subnum)
  
  bc_rt_draws = data_frame()
  bc_rt_ppc = data_frame()
  
  for(i in 1:length(subnums)){
    cur_sub = subnums[i]
    
    cur_bc_data = data_bc_clean %>% 
      ungroup() %>%
      filter(subnum == cur_sub) %>%
      select(abs_val_diff_std, day_std, type, abs_val_diff, day, log_rt)
    
    
    cur_bc_rt <- brm(formula = log_rt ~ abs_val_diff_std * day_std * type,
                        data= cur_bc_data,
                        warmup = 500,
                        iter = 2500,
                        chains = 4,
                        init = "0",
                        cores = 4,
                        seed = 389253)
    
    cur_draws = as_draws_df(cur_bc_rt)
    cur_draws$subnum = cur_sub
    
    bc_rt_draws = rbind(bc_rt_draws, cur_draws)
    
    cur_pred = fitted(cur_bc_rt, newdata = cur_bc_data %>%
                        select(-abs_val_diff, -day, -log_rt)) %>% 
      as_tibble() %>%
      transmute(pred_log_rt = Estimate) %>% #same as mean brms::posterior_epred values not brms::posterior_predict
      bind_cols(cur_bc_data) %>%
      mutate(subnum = cur_sub)
    
    bc_rt_ppc = rbind(bc_rt_ppc, cur_pred)
  }
  names(bc_rt_draws) = gsub(":", ".", names(bc_rt_draws))
  write.csv(bc_rt_draws, fn_draws, row.names = F)
  write.csv(bc_rt_ppc, fn_ppc, row.names = F)
  
  rm(cur_bc_data, cur_bc_rt, cur_draws, cur_pred)
}

```

Examine chains for the three variables of interest  

```{r}
as.data.frame(bc_rt_draws) %>%
  select("b_abs_val_diff_std.day_std", "b_abs_val_diff_std.typeRE", "b_abs_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  ggplot(aes(.iteration, value, color = as.factor(.chain)))+
  geom_line()+
  facet_grid(subnum ~ key, scales = 'free_y')+
  labs(x = "", y = "") +
  theme(legend.position = "none",
        panel.grid = element_blank(),
        axis.ticks = element_blank(),
        axis.text = element_blank())
  
```

Examine autocorrelation in the variables of interest.  

```{r}
as.data.frame(bc_rt_draws) %>%
  select("b_abs_val_diff_std.day_std", "b_abs_val_diff_std.typeRE", "b_abs_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  group_by(subnum, .chain, key) %>%
  summarise(lag0 = acf(value, lag.max=1, plot = F)[["acf"]][1],
            lag1 = acf(value, lag.max=1, plot = F)[["acf"]][2],
            lag2 = acf(value, lag.max=2, plot = F)[["acf"]][3],
            lag3 = acf(value, lag.max=3, plot = F)[["acf"]][4],
            lag4 = acf(value, lag.max=4, plot = F)[["acf"]][5],
            lag5 = acf(value, lag.max=5, plot = F)[["acf"]][6],
            lag6 = acf(value, lag.max=6, plot = F)[["acf"]][7],
            lag7 = acf(value, lag.max=7, plot = F)[["acf"]][8],
            lag8 = acf(value, lag.max=8, plot = F)[["acf"]][9],
            lag9 = acf(value, lag.max=9, plot = F)[["acf"]][10],
            lag10 = acf(value, lag.max=10, plot = F)[["acf"]][11],
            lag11 = acf(value, lag.max=11, plot = F)[["acf"]][12], .groups = 'keep') %>%
  gather(lag, cor, -subnum, -.chain, -key) %>%
  mutate(lag = gsub("lag", "", lag),
         lag = as.numeric(lag)) %>%
  ggplot(aes(lag, cor, fill = as.factor(.chain)))+
  geom_bar(stat = "identity", alpha=.5, position = "identity", color = NA)+
  facet_grid(subnum ~ key)+
  labs(x = "Lag", y = "Correlation") +
  theme(legend.position = "none",
        panel.grid = element_blank())+
  scale_x_continuous(breaks = c(0, 5, 10))+
  scale_y_continuous(breaks = c(0, .5, 1))
```

```{r}
p = as.data.frame(bc_rt_draws) %>%
  # select("b_abs_val_diff_std.day_std", "b_abs_val_diff_std.typeRE", "b_abs_val_diff_std.day_std.typeRE", "b_abs_val_diff_std", "b_day_std", "b_typeRE" , subnum, .chain, .iteration) %>%
  select("b_abs_val_diff_std.day_std", "b_abs_val_diff_std.typeRE", "b_abs_val_diff_std.day_std.typeRE", subnum, .chain, .iteration) %>%
  gather(key, value, -subnum, -.chain, -.iteration) %>%
  mutate(key = ifelse(key == "b_abs_val_diff_std.day_std", "|Value Diff| * Day", ifelse(key == "b_abs_val_diff_std.typeRE", "|Value Diff| * Type", ifelse(key == "b_abs_val_diff_std.day_std.typeRE", "|Value Diff| * Day * Type", NA))),
         key = factor(key, levels = c("|Value Diff| * Type", "|Value Diff| * Day", "|Value Diff| * Day * Type"))) %>%
  ggplot(aes(value, fill = as.factor(subnum))) +
  geom_density(position="identity", alpha=.75, color=NA) +
  geom_vline(aes(xintercept = 0), color = "light gray") + 
  facet_wrap(~key) +
  # facet_grid(subnum~key) +
  labs(x = "Parameter Estimate", y = "", fill = "Subject") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks = c(0)) +
  guides(fill=guide_legend(nrow=1))

p
ggsave(file=paste0(fig_out_path, 'bc_rt_interactionParEsts.jpg'), p, height = 3, width = 9, units="in")
```

```{r}
p = data_bc_clean %>%
  mutate(abs_val_diff_bin_str =  paste0(abs(val_diff_bin)*50-25,":",abs(val_diff_bin)*50+25),
         abs_val_diff_bin_str = ifelse(abs_val_diff_bin_str ==  "-25:25", "0:25", abs_val_diff_bin_str),
         abs_val_diff_bin_str = factor(abs_val_diff_bin_str, levels = c("0:25", "25:75", "75:125", "125:175", "175:225", "225:275"))) %>%
  group_by(subnum, week, abs_val_diff_bin_str, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            .groups="keep") %>%
  ungroup() %>%
  group_by(week, abs_val_diff_bin_str, type) %>%
  summarise(sem_log_rt = sd(mean_log_rt)/sqrt(n()),
            mean_log_rt = mean(mean_log_rt), .groups = "keep") %>%
  ggplot(aes(abs_val_diff_bin_str, mean_log_rt, color=type))+
  geom_point(size = 2.5)+
  geom_errorbar(aes(ymin=mean_log_rt-sem_log_rt, ymax=mean_log_rt+sem_log_rt), width=0, size = 1)+
  geom_line(aes(group=type))+
  facet_grid(.~week)+
  labs(x = "|Value Left - Value Right|", y = "Mean Log RT", title="BC Task", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")+
  # scale_x_discrete(labels=c("-225:-175", "", "-125:-75", "", "-25:25", "", "75:125", "", "175:225"))+
  scale_y_continuous(breaks = seq(-1,.5,.5))

p
# ggsave(file=paste0(fig_out_path, 'bc_group_RTOverAbsValDiff.jpg'), p, height = 3, width=9, units="in")
```

Plot predicted over true

```{r}
bc_data_summary = data_bc_clean %>%
  mutate(abs_val_diff_bin_str =  paste0(abs(val_diff_bin)*50-25,":",abs(val_diff_bin)*50+25),
         abs_val_diff_bin_str = ifelse(abs_val_diff_bin_str ==  "-25:25", "0:25", abs_val_diff_bin_str),
         abs_val_diff_bin_str = factor(abs_val_diff_bin_str, levels = c("0:25", "25:75", "75:125", "125:175", "175:225", "225:275")),
         abs_val_diff_bin_midpoint = round(abs(val_diff)/50)*50) %>%
  group_by(subnum, day, abs_val_diff_bin_str, type) %>%
  summarise(mean_log_rt = mean(log(rt)),
            sem_log_rt = sd(log(rt))/sqrt(n()),
            abs_val_diff = unique(abs_val_diff_bin_midpoint),
            .groups="keep") %>%
  filter(day %in% c(1, 3, 7, 11)) %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 3", "Day 7", "Day 11")))

p = bc_rt_ppc %>% 
  filter(day %in% c(1, 3, 7, 11)) %>%
  mutate(day = paste0("Day ", day),
         day = factor(day, levels = c("Day 1", "Day 3", "Day 7", "Day 11"))) %>%
  ggplot()+
  geom_line(aes(x = abs_val_diff, y = pred_log_rt, color=type))+
  geom_point(data = bc_data_summary, aes(x = abs_val_diff, y = mean_log_rt, color = type)) +
  geom_errorbar(data = bc_data_summary, aes(x = abs_val_diff, y = mean_log_rt, ymin = mean_log_rt - sem_log_rt, ymax = mean_log_rt + sem_log_rt, color= type), width = 0) +
  facet_grid(subnum~day) + 
  labs(x = "|Value Left - Value Right|", y = "Log RT", title="BC Task - True vs Predicted", color="")+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(angle = 15, margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_color_brewer(palette = "Dark2")

# ggsave(file=paste0(fig_out_path, 'bc_rt_ppc.jpg'), p, height = 6, width = 10, units="in")
p
```

# DDM for YN

```{r}

```

# aDDM for BC

```{r}

```
