---
title: "Novel vs. repeated choice project: DDM posterior predictive checks and simulations for tradeoffs"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(here)
library(brms)
library(gridExtra)
theme_set(theme_bw())
helpers_path = paste0(here(),'/analysis/helpers/')
fig_out_path = paste0(here(), '/outputs/fig/')
```

Add columns that will be used for plots below.

```{r}
source(paste0(helpers_path, '01_clean_behavioral_data.R'))

rm(data_bc_clean)

data_yn_clean = data_yn_clean %>%
  mutate(correct = ifelse(possiblePayoff>reference & yesChosen == 1, 1, ifelse(possiblePayoff < reference & yesChosen == 0, 1, 0))) %>%
  mutate(type = ifelse(type == 1, "HT", "RE"),
         week = ifelse(week == 1, "Week 1", ifelse(week == 2, "Week 2", ifelse(week == 3, "Week 3", NA))),
         week = factor(week, levels = c("Week 1", "Week 2", "Week 3"))) %>%
  mutate(val_diff = possiblePayoff - reference,
         val_diff_bin = round(val_diff/50),
         val_diff_bin_str = paste0(val_diff_bin*50-25,":",val_diff_bin*50+25),
         val_diff_bin_str = factor(val_diff_bin_str, levels = c("-225:-175", "-175:-125", "-125:-75", "-75:-25", "-25:25", "25:75", "75:125", "125:175", "175:225")))
```

# YN Task

Read in parameter estimates. This contains all 30000 samples per parameter for each subject and day. Takes a while to read in.

```{r eval = FALSE}
fn = file.path(here(), "inputs",'yn_hddm_mcmc_draws.csv')

if(file.exists(fn)){
  all_results_df = read.csv(fn)
  
} else{
  stim_types = c("HT", "RE")
  days = as.character(seq(1,11,1))
  
  in_path = file.path(here(), "inputs")
  
  all_results_df = data.frame()
  
  for(i in 1:length(stim_types)) {
    for(j in 1:length(days)) {
      
      cur_stim_type = stim_types[i]
      cur_day = days[j]
      
      fn = file.path(in_path, paste0('results_YN_HDDM_FIT_', cur_stim_type,'_day_', cur_day,'.RData'))
      
      if(file.exists(fn)) {
        
        load(fn)
        
        cur_results_df = data.frame()
        for(k in 1:length(results$mcmc)){
          cur_chain = as.data.frame(results$mcmc[[k]])
          cur_results_df = rbind(cur_results_df, cur_chain)
        }
        
        cur_results_df = cur_results_df %>%
          gather(par, estimate) %>%
          filter(grepl("\\[", par)) %>%
          mutate(type = cur_stim_type,
                 day = cur_day)
        
        cur_results_df = cur_results_df %>%
          separate(par, c("a", "b"), sep = '\\.', remove = F, fill = "right") %>%
          separate(a, c("c", "d"), sep = "\\[", remove = F, fill = "right") %>%
          select(-a) %>%
          mutate(d = paste0('p[',d)) %>%
          mutate(b = ifelse(is.na(b), d, b)) %>%
          select(-d, -par) %>%
          rename(par_name = c, subnum = b) %>%
          mutate(par_name = ifelse(par_name == "theta", "ndt", ifelse(par_name == "b", "d", ifelse(par_name == "alpha", "sigma", par_name))),
                 subnum = ifelse(subnum == 'p[1]', "601", ifelse(subnum == "p[2]", "609", ifelse(subnum == 'p[3]', "611", ifelse(subnum == "p[4]", "619", ifelse(subnum == "p[5]", "621", ifelse(subnum == "p[6]", "629", subnum)))))),
                 day = as.numeric(day))
        
        all_results_df = rbind(all_results_df, cur_results_df)
        
      } else {
        next
      }
    }
  }
  fn = file.path(here(), "inputs",'yn_hddm_mcmc_draws.csv')
  write.csv(all_results_df, fn, row.names = F)
  rm(cur_chain, cur_results_df, results, cur_day, cur_stim_type, days, fn, i, j, k, stim_types)
}



```

## Correlations between estimates

```{r}
all_d_sigma = all_results_df %>%
  filter(par_name %in% c("d", "sigma"))

rm(all_results_df)
```

```{r}
subs = c('601', '609', '611', '619', '621', '629')
types = c('HT', 'RE')
days = seq(1,11,1)

d_sigma_cors =  data.frame(subnum = NA, type = NA, day = NA, cor = NA)

for (i in 1:length(subs)){
  for (j in 1:length(types)){
    for (k in 1:length(days)){
      
      cur_sub = subs[i]
      cur_type = types[j]
      cur_day = days[k]
      
      cur_ds = all_d_sigma %>%
        filter(subnum == cur_sub & type == cur_type & day == cur_day & par_name == "d") %>%
        select(estimate)
      
      cur_sigmas = all_d_sigma %>%
        filter(subnum == cur_sub & type == cur_type & day == cur_day & par_name == "sigma") %>%
        select(estimate)
      
      cur_cor = round(cor(cur_ds, cur_sigmas), 3)
      
      cur_row = data.frame(subnum = cur_sub, type = cur_type, day = cur_day, cor = as.numeric(cur_cor))
      
      d_sigma_cors = rbind(d_sigma_cors, cur_row)
    }
  }
}


d_sigma_cors = d_sigma_cors %>%
  drop_na()
```

```{r}
p = d_sigma_cors %>%
  ggplot(aes(type, cor, fill=type))+
  geom_boxplot()+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_fill_brewer(palette = "Dark2")+
  labs(x = "", fill = "", y = "Correlation between d and sigma estimates")

# ggsave(file=paste0(fig_out_path, 'yn_ddm_d_sigma_cor.jpg'), p, height = 5, width = 5, units="in")
```

## RT by response

```{r}
p = data_yn_clean %>%
  filter(rt < 3) %>%
  select(subnum, day, type, yesChosen, rt) %>%
  mutate(rt = ifelse(yesChosen == 0, rt*(-1), rt),
         day = paste0("Day ", day),
         day = factor(day, levels = paste0("Day ", seq(1,11, 1)))) %>%
  ggplot(aes(rt, fill = type))+
  geom_density(position = "identity", alpha = .5, color = NA)+
  facet_grid(subnum ~ day)+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  geom_vline(aes(xintercept = 0), color = "gray") +
  scale_fill_brewer(palette = "Dark2")+
  labs(y = "", fill = "")

p
# ggsave(file=paste0(fig_out_path, 'yn_ddm_raw_rt_dists.jpg'), p, height = 10, width = 18, units="in")
```

## Posterior predictive checks

### Predicted data accounting for posterior uncertainty

With 1000 samples from posteriors to account for uncertainty in estimates.

```{r eval=FALSE}

# Takes a while
inpath = '/Users/zeynepenkavi/CpuEaters/NovelVsRepeated/behavior/inputs'

conds = c('HT')
subs = c('609','621')

# conds = c('HT', 'RE')
# subs = c('601', '609','611', '619', '621', '629')
days = seq(1, 11, 1)


for (k in 1:length(conds)){
  cur_cond = conds[k]
  
  for (j in 1:length(subs)){
    cur_sub = subs[j]
    
    for (i in 1:length(days)){
      cur_day = days[i]
      fn = file.path(inpath, paste0("yn_sim_ddm_sub-", cur_sub, "_", cur_cond, "_day-", cur_day, ".csv"))
      
      if(!file.exists(fn)){
        next
      } else{
        tmp = read.csv(fn)
      }
      
      
      if(i == 1){
        sub_cond_sim_data = tmp
      } else {
        sub_cond_sim_data = rbind(sub_cond_sim_data, tmp)
      }
    }
    fill_col = ifelse(cur_cond == "HT", "#1B9E77", "#D95F02")
    
    p = sub_cond_sim_data %>%
      filter(rt < 3 & pred_rt < 3) %>%
      mutate(rt = ifelse(yesChosen == 1, rt, rt*(-1)),
             pred_rt = ifelse(pred_yesChosen == 1, pred_rt, pred_rt*(-1)), 
             day = paste0("Day ", day),
             day = factor(day, levels = paste0("Day ", seq(1,11, 1)))) %>%
      ggplot()+
      geom_density(aes(x = pred_rt), position = "identity", alpha = .5) +
      geom_histogram(aes(x = rt, y = ..density..), bins = 30,  position = "identity", alpha = .5, color = NA, fill = fill_col)+
      facet_grid(subnum ~ day)+
      theme(panel.grid = element_blank(),
            axis.text = element_blank(),
            axis.ticks = element_blank())+
      geom_vline(aes(xintercept = 0), color = "gray") +
      labs(y = "", x = "")
    
    fn = paste0(fig_out_path,'yn_ddm_sim_rt_ppc_sub-',cur_sub, '_cond-',cur_cond, '.jpg')
    print(paste("Saving", fn))
    ggsave(file = fn, p, height = 2, width = 18, units="in") 
    
  }
}


```

### Mean a posteriori data

Does mean a posteriori data capture other choice and RT patterns?

Read in parameter posterior summaries and organize them

```{r}
stim_types = c("HT", "RE")
days = as.character(seq(1,11,1))

in_path = file.path(here(), "inputs")

yn_ddm_summary = data.frame()

for(i in 1:length(stim_types)){
  for(j in 1:length(days)){
    
    cur_stim_type = stim_types[i]
    cur_day = days[j]
    
    if(file.exists(file.path(in_path, paste0('summary_YN_HDDM_FIT_', cur_stim_type,'_day_', cur_day,'.csv')))){
      cur_summary = read.csv(file.path(in_path, paste0('summary_YN_HDDM_FIT_', cur_stim_type,'_day_', cur_day,'.csv')))
      cur_summary = cur_summary %>%
        rename(par = X) %>%
        mutate(stim_type = cur_stim_type,
               day = cur_day)
      
      yn_ddm_summary = rbind(yn_ddm_summary, cur_summary)
    } else {
      next
    }
  }
}
```

```{r}
yn_ddm_summary = yn_ddm_summary %>%
  select(par, Mean, day, stim_type ) %>%
  separate(par, c("a", "b"), sep = '\\.', remove = F, fill = "right") %>%
  separate(a, c("c", "d"), sep = "\\[", remove = F, fill = "right") %>%
  select(-a) %>%
  mutate(d = paste0('p[',d)) %>%
  mutate(b = ifelse(is.na(b), d, b)) %>%
  select(-d, -par) %>%
  rename(par_name = c, par_group = b) %>%
  mutate(par_name = ifelse(par_name == "theta", "ndt", ifelse(par_name == "b", "d", ifelse(par_name == "alpha", "sigma", par_name))),
         par_group = ifelse(par_group == 'p[1]', "601", ifelse(par_group == "p[2]", "609", ifelse(par_group == 'p[3]', "611", ifelse(par_group == "p[4]", "619", ifelse(par_group == "p[5]", "621", ifelse(par_group == "p[6]", "629", par_group)))))),
         day = as.numeric(day)) %>%
  filter(par_name != "deviance") %>%
  filter(par_group != "kappa" & par_group != "pr") %>%
  filter(par_group != "mu") %>% #Not showing group estimates in this plot
  mutate(par_name = factor(par_name, levels = c("d", "sigma", "bias", "ndt")))
```

Simulation helper functions

```{r}
sim_trial = function(trial_vdiff, sampled_sigma, sampled_d, sampled_ndt, sampled_bias){

  # Multiplying boundary separation and drift rate my sigma to account for that parameter
  trial_drift = sampled_sigma * (sampled_d * trial_vdiff)

  if(abs(trial_drift) < 10){
    cur_pred = RWiener::rwiener(1, 2*sampled_sigma, sampled_ndt, sampled_bias, trial_drift)
  } else {
    print("d too large. Sampling RT.")
    pq = sampled_ndt + abs(rnorm(1, mean = 0, sd = 0.01))
    pr = ifelse(trial_drift>10, factor("upper", levels = c("upper", "lower")), factor("lower", levels = c("upper", "lower")))
    cur_pred = data.frame(q = pq, resp = pr)
  }
  return(cur_pred)

}

sim_subj_cond_day_once = function(cur_stims, sampled_sigma, sampled_d, sampled_ndt, sampled_bias){

  pred_data = cur_stims
  pred_data$sampled_sigma = sampled_sigma
  pred_data$sampled_d = sampled_d
  pred_data$sampled_ndt = sampled_ndt
  pred_data$sampled_bias = sampled_bias
  pred_data$pred_rt = NA
  pred_data$pred_yesChosen = NA

  for(i in 1:nrow(cur_stims)){

    trial_vdiff = cur_stims$possiblePayoff[i] - cur_stims$reference[i]
    cur_pred = sim_trial(trial_vdiff, sampled_sigma, sampled_d, sampled_ndt, sampled_bias)

    pred_data$pred_rt[i] = cur_pred$q
    pred_data$pred_yesChosen[i] = cur_pred$resp

  }

  return(pred_data)
}
```

```{r}
conds = c('HT', 'RE')
subs = c('601', '609','611', '619', '621', '629')
days = seq(1, 11, 1)

for(i in 1:length(conds)){
  cur_type = conds[i]
  
  for (j in 1:length(subs)){
    cur_sub = subs[j]
    
    for (k in 1:length(days)){
      cur_day = days[k]
      
      cur_stims = data_yn_clean %>%
        filter(subnum == cur_sub & day == cur_day & type == cur_type) %>%
        select(subnum, day, type, possiblePayoff, reference, yesChosen, rt)
      
      cur_pars = yn_ddm_summary %>%
        filter(par_group == cur_sub & day == cur_day & stim_type == cur_type) %>%
        select(par_name, Mean) %>%
        spread(par_name, Mean)
      
      cur_pred = sim_subj_cond_day_once(cur_stims, cur_pars$sigma, cur_pars$d, cur_pars$ndt, cur_pars$bias)
      
      if(!exists("sim_yn_map")){
        sim_yn_map = cur_pred
      } else{
        sim_yn_map = rbind(sim_yn_map, cur_pred)
      }
    }
  }
}
```

```{r}
rm(cur_pars, cur_pred, cur_stims, cur_summary, cur_day, cur_stim_type, cur_Sub, cur_type)
rm(i, j, k)
```

Check RT/Choice plots look similar to the simulated data using samples from the posterior

```{r}
cur_cond = 'HT'
fill_col = ifelse(cur_cond == "HT", "#1B9E77", "#D95F02")

sim_yn_map %>%
  filter(type == cur_cond) %>%
  filter(rt < 3 & pred_rt < 3) %>%
  mutate(rt = ifelse(yesChosen == 1, rt, rt*(-1)),
         pred_rt = ifelse(pred_yesChosen == 1, pred_rt, pred_rt*(-1)), 
         day = paste0("Day ", day),
         day = factor(day, levels = paste0("Day ", seq(1,11, 1)))) %>%
  ggplot()+
  geom_density(aes(x = pred_rt), position = "identity", alpha = .5) +
  geom_histogram(aes(x = rt, y = ..density..), bins = 30,  position = "identity", alpha = .5, color = NA, fill = fill_col)+
  facet_grid(subnum ~ day)+
  theme(panel.grid = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())+
  geom_vline(aes(xintercept = 0), color = "gray") +
  labs(y = "", x = "")
```

```{r}
cur_cond = 'RE'
fill_col = ifelse(cur_cond == "HT", "#1B9E77", "#D95F02")

sim_yn_map %>%
  filter(type == cur_cond) %>%
  filter(rt < 3 & pred_rt < 3) %>%
  mutate(rt = ifelse(yesChosen == 1, rt, rt*(-1)),
         pred_rt = ifelse(pred_yesChosen == 1, pred_rt, pred_rt*(-1)), 
         day = paste0("Day ", day),
         day = factor(day, levels = paste0("Day ", seq(1,11, 1)))) %>%
  ggplot()+
  geom_density(aes(x = pred_rt), position = "identity", alpha = .5) +
  geom_histogram(aes(x = rt, y = ..density..), bins = 30,  position = "identity", alpha = .5, color = NA, fill = fill_col)+
  facet_grid(subnum ~ day)+
  theme(panel.grid = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())+
  geom_vline(aes(xintercept = 0), color = "gray") +
  labs(y = "", x = "")
```

What are the other choice and RT patterns the predicted data should capture?

### Value difference on choice

Choice:
- Slope of value difference on choice logit always positive?
- Slope of value difference on choice logit smaller for RE than HT?
- Slope of value difference on choice logit increases with days?
- Slope of value difference on choice logit increases less for RE than HT with days?
- Is the value difference effect nonlinear?

### Value difference on RT

RT: 
- Is the RT jump from day 1 to day 2 largest
- Slope of absolute value difference on RT is negative?
- Slope of absolute value difference on RT smaller for RE than HT?


-------------------------------------------------------------------------------

Tradeoff simulations????
