---
title: "Novel vs. repeated choice project: DDM posterior predictive checks and simulations for tradeoffs"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: 'hide'
---

# Set up environment and load in data

```{r include=FALSE}
library(tidyverse)
library(here)
library(brms)
library(gridExtra)
theme_set(theme_bw())
helpers_path = paste0(here(),'/analysis/helpers/')
fig_out_path = paste0(here(), '/outputs/fig/')
```

Add columns that will be used for plots below.

```{r}
source(paste0(helpers_path, '01_clean_behavioral_data.R'))

data_yn_clean = data_yn_clean %>%
  mutate(correct = ifelse(possiblePayoff>reference & yesChosen == 1, 1, ifelse(possiblePayoff < reference & yesChosen == 0, 1, 0))) %>%
  mutate(type = ifelse(type == 1, "HT", "RE"),
         week = ifelse(week == 1, "Week 1", ifelse(week == 2, "Week 2", ifelse(week == 3, "Week 3", NA))),
         week = factor(week, levels = c("Week 1", "Week 2", "Week 3"))) %>%
  mutate(val_diff = possiblePayoff - reference,
         val_diff_bin = round(val_diff/50),
         val_diff_bin_str = paste0(val_diff_bin*50-25,":",val_diff_bin*50+25),
         val_diff_bin_str = factor(val_diff_bin_str, levels = c("-225:-175", "-175:-125", "-125:-75", "-75:-25", "-25:25", "25:75", "75:125", "125:175", "175:225")))

data_bc_clean = data_bc_clean %>%
  mutate(correct = ifelse(possiblePayoffleft>possiblePayoffright & leftChosen == 1, 1, ifelse(possiblePayoffleft<possiblePayoffright & leftChosen == 0, 1, 0))) %>%
  mutate(type = ifelse(typeLeft == 1, "HT", "RE"),
         week = ifelse(week == 1, "Week 1", ifelse(week == 2, "Week 2", ifelse(week == 3, "Week 3", NA))),
         week = factor(week, levels = c("Week 1", "Week 2", "Week 3"))) %>%
  mutate(val_diff = possiblePayoffleft - possiblePayoffright,
         val_diff_bin = round(val_diff/50),
         val_diff_bin_str = paste0(val_diff_bin*50-25,":",val_diff_bin*50+25),
         val_diff_bin_str = factor(val_diff_bin_str, levels = c("-275:-225","-225:-175", "-175:-125", "-125:-75", "-75:-25", "-25:25", "25:75", "75:125", "125:175", "175:225", "225:275"))) %>%
  filter(!is.na(val_diff_bin_str))
```

# YN Task

Read in parameter estimates

```{r eval = FALSE}
fn = file.path(here(), "inputs",'yn_hddm_mcmc_draws.csv')

if(file.exists(fn)){
  all_results_df = read.csv(fn)

} else{
  stim_types = c("HT", "RE")
  days = as.character(seq(1,11,1))
  
  in_path = file.path(here(), "inputs")
  
  all_results_df = data.frame()
  
  for(i in 1:length(stim_types)) {
    for(j in 1:length(days)) {
      
      cur_stim_type = stim_types[i]
      cur_day = days[j]
      
      fn = file.path(in_path, paste0('results_YN_HDDM_FIT_', cur_stim_type,'_day_', cur_day,'.RData'))
      
      if(file.exists(fn)) {
        
        load(fn)
        
        cur_results_df = data.frame()
        for(k in 1:length(results$mcmc)){
          cur_chain = as.data.frame(results$mcmc[[k]])
          cur_results_df = rbind(cur_results_df, cur_chain)
        }
        
        cur_results_df = cur_results_df %>%
          gather(par, estimate) %>%
          filter(grepl("\\[", par)) %>%
          mutate(type = cur_stim_type,
                 day = cur_day)
        
        cur_results_df = cur_results_df %>%
          separate(par, c("a", "b"), sep = '\\.', remove = F, fill = "right") %>%
          separate(a, c("c", "d"), sep = "\\[", remove = F, fill = "right") %>%
          select(-a) %>%
          mutate(d = paste0('p[',d)) %>%
          mutate(b = ifelse(is.na(b), d, b)) %>%
          select(-d, -par) %>%
          rename(par_name = c, subnum = b) %>%
          mutate(par_name = ifelse(par_name == "theta", "ndt", ifelse(par_name == "b", "d", ifelse(par_name == "alpha", "sigma", par_name))),
                 subnum = ifelse(subnum == 'p[1]', "601", ifelse(subnum == "p[2]", "609", ifelse(subnum == 'p[3]', "611", ifelse(subnum == "p[4]", "619", ifelse(subnum == "p[5]", "621", ifelse(subnum == "p[6]", "629", subnum)))))),
                 day = as.numeric(day))
        
        all_results_df = rbind(all_results_df, cur_results_df)
        
      } else {
        next
      }
    }
  }
  fn = file.path(here(), "inputs",'yn_hddm_mcmc_draws.csv')
  write.csv(all_results_df, fn, row.names = F)
  rm(cur_chain, cur_results_df, results, cur_day, cur_stim_type, days, fn, i, j, k, stim_types)
}



```

### Correlations between estimates

```{r}
all_d_sigma = all_results_df %>%
  filter(par_name %in% c("d", "sigma"))

rm(all_results_df)
```

```{r}
subs = c('601', '609', '611', '619', '621', '629')
types = c('HT', 'RE')
days = seq(1,11,1)

d_sigma_cors =  data.frame(subnum = NA, type = NA, day = NA, cor = NA)

for (i in 1:length(subs)){
  for (j in 1:length(types)){
    for (k in 1:length(days)){
     
      cur_sub = subs[i]
      cur_type = types[j]
      cur_day = days[k]
      
      cur_ds = all_d_sigma %>%
        filter(subnum == cur_sub & type == cur_type & day == cur_day & par_name == "d") %>%
        select(estimate)
      
      cur_sigmas = all_d_sigma %>%
        filter(subnum == cur_sub & type == cur_type & day == cur_day & par_name == "sigma") %>%
        select(estimate)
      
      cur_cor = round(cor(cur_ds, cur_sigmas), 3)
      
      cur_row = data.frame(subnum = cur_sub, type = cur_type, day = cur_day, cor = as.numeric(cur_cor))
        
      d_sigma_cors = rbind(d_sigma_cors, cur_row)
    }
  }
}


d_sigma_cors = d_sigma_cors %>%
  drop_na()
```

```{r}
p = d_sigma_cors %>%
  ggplot(aes(type, cor, fill=type))+
  geom_boxplot()+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  scale_fill_brewer(palette = "Dark2")+
  labs(x = "", fill = "", y = "Correlation between d and sigma estimates")

# ggsave(file=paste0(fig_out_path, 'yn_ddm_d_sigma_cor.jpg'), p, height = 5, width = 5, units="in")
```

## RT by response

```{r}
p = data_yn_clean %>%
  filter(rt < 3) %>%
  select(subnum, day, type, yesChosen, rt) %>%
  mutate(rt = ifelse(yesChosen == 0, rt*(-1), rt),
         day = paste0("Day ", day),
         day = factor(day, levels = paste0("Day ", seq(1,11, 1)))) %>%
  ggplot(aes(rt, fill = type))+
  geom_density(position = "identity", alpha = .5, color = NA)+
  facet_grid(subnum ~ day)+
  theme(panel.grid = element_blank(),
        legend.position = "bottom",
        axis.text.x = element_text(margin = margin(t = 5)),
        legend.box.margin=margin(t = -10))+
  geom_vline(aes(xintercept = 0), color = "gray") +
  scale_fill_brewer(palette = "Dark2")+
  labs(y = "", fill = "")

p
# ggsave(file=paste0(fig_out_path, 'yn_ddm_raw_rt_dists.jpg'), p, height = 10, width = 18, units="in")
```

### Posterior predictive RTs

```{r}
inpath = '/Users/zeynepenkavi/CpuEaters/NovelVsRepeated/behavior/inputs'


conds = c('HT', 'RE')
# subs = c('609', '621', '629')
subs = c('601', '611', '619')
days = seq(1, 11, 1)


for (k in 1:length(conds)){
  cur_cond = conds[k]
  
  for (j in 1:length(subs)){
    cur_sub = subs[j]
    
    for (i in 1:length(days)){
      cur_day = days[i]
      fn = file.path(inpath, paste0("yn_sim_ddm_sub-", cur_sub, "_", cur_cond, "_day-", cur_day, ".csv"))
      
      if(!file.exists(fn)){
        next
      } else{
        tmp = read.csv(fn)
      }
      
      
      if(i == 1){
        sub_cond_sim_data = tmp
      } else {
        sub_cond_sim_data = rbind(sub_cond_sim_data, tmp)
      }
    }
    fill_col = ifelse(cur_cond == "HT", "#1B9E77", "#D95F02")
    
    p = sub_cond_sim_data %>%
      filter(rt < 3 & pred_rt < 3) %>%
      mutate(rt = ifelse(yesChosen == 1, rt, rt*(-1)),
             pred_rt = ifelse(pred_yesChosen == 1, pred_rt, pred_rt*(-1)), 
             day = paste0("Day ", day),
             day = factor(day, levels = paste0("Day ", seq(1,11, 1)))) %>%
      ggplot()+
      geom_density(aes(x = pred_rt), position = "identity", alpha = .5) +
      geom_histogram(aes(x = rt, y = ..density..), bins = 30,  position = "identity", alpha = .5, color = NA, fill = fill_col)+
      facet_grid(subnum ~ day)+
      theme(panel.grid = element_blank(),
            axis.text = element_blank(),
            axis.ticks = element_blank())+
      geom_vline(aes(xintercept = 0), color = "gray") +
      labs(y = "", x = "")
    
    fn = paste0(fig_out_path,'yn_ddm_sim_rt_ppc_sub-',cur_sub, '_cond-',cur_cond, '.jpg')
    print(paste("Saving", fn))
    ggsave(file = fn, p, height = 2, width = 18, units="in") 
    
  }
}


```

#### Debug failed jobs

Is it a filtering issue?

```{r}
conds = c('HT', 'RE')
subs = c(601, 609, 611, 619, 621, 629)
days = seq(1, 11, 1)

for(i in 1:length(conds)){
  cur_cond = conds[i]
  
  for(j in 1:length(subs)){
    cur_sub = subs[j]
    
    for(k in 1:length(days)){
    cur_day = days[k]
    
    tmp = data_yn_clean %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_cond)
    
    print(paste0("N Rows for sub-", cur_sub, " day-", cur_day, " cond-", cur_cond, ": ", nrow(tmp)))
    
    }
  }
}
```

```{r}
conds = c('HT', 'RE')
subs = c(601, 609, 611, 619, 621, 629)
days = seq(1, 11, 1)

for(i in 1:length(conds)){
  cur_cond = conds[i]
  
  for(j in 1:length(subs)){
    cur_sub = subs[j]
    
    for(k in 1:length(days)){
    cur_day = days[k]
    
    tmp = all_results_df %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_cond)
    
    print(paste0("N Pars sub-", cur_sub, " day-", cur_day, " cond-", cur_cond, ": ", nrow(tmp)/30000))
    
    }
  }
}
```

```{r}
cur_sub = 601
cur_day = 8
cur_cond = "HT"

tmp = all_results_df %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_cond)

unique(tmp$subnum)
```

```{r}
subnum = 601
day = 8
cond = "HT"

tmp = all_results_df %>%
      filter(subnum == subnum & day == day & type == cond)

unique(tmp$subnum)
```

Is it a parameter value issues?

```{r}
cur_sub = 601
cur_day = 8
cur_cond = "HT"

tmp = all_results_df %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_cond) %>%
  filter(par_name == "d")

summary(tmp$estimate)

tmp = all_results_df %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_cond) %>%
  filter(par_name == "sigma")

summary(tmp$estimate)

tmp = all_results_df %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_cond) %>%
  filter(par_name == "ndt")

summary(tmp$estimate)

tmp = all_results_df %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_cond) %>%
  filter(par_name == "bias")

summary(tmp$estimate)
```

Single iteration debugging found these parameters problematic:

```{r}
sampled_bias = 0.514
sampled_d = 0.0665
sampled_ndt = 0.351
# sampled_sigma = 1.45
sampled_sigma = 1.32

# sampled_bias = 0.522
# sampled_d = 0.0624
# sampled_ndt = 0.357
# sampled_sigma = 1.32

cur_sub = 601
cur_day = 8
cur_type = "HT"

cur_stims = data_yn_clean %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_type) %>%
      select(subnum, day, type, possiblePayoff, reference, yesChosen, rt)

sim_subj_cond_day_once(cur_stims, sampled_sigma, sampled_d, sampled_ndt, sampled_bias)
```

```{r}
sampled_bias = 0.514
sampled_d = 0.0665
sampled_ndt = 0.351
sampled_sigma = 1.45

for (i in 1:nrow(cur_stims)){
  trial_vdiff = cur_stims$possiblePayoff[i] - cur_stims$reference[i]
  
  trial_drift = sampled_sigma * (sampled_d * trial_vdiff)
  
  print(i) #stuck at 275
  RWiener::rwiener(1, 2*sampled_sigma, sampled_ndt, sampled_bias, trial_drift)
}

```

```{r}
i = 275
# trial_vdiff = cur_stims$possiblePayoff[i] - cur_stims$reference[i]
trial_vdiff = 160
trial_drift = sampled_sigma * (sampled_d * trial_vdiff)
RWiener::rwiener(1, 2*sampled_sigma, sampled_ndt, sampled_bias, trial_drift)
```
Is it because when the drift rate is so high it tries to predict a very short rt but it's not allowed due to the sampled ndt?

```{r}
RWiener::dwiener(q = sampled_ndt+10e-1, 2*sampled_sigma, sampled_ndt, sampled_bias, trial_drift, resp = "upper")
```

```{r}
sampled_bias = 0.522
sampled_d = 0.0624
sampled_ndt = 0.357
sampled_sigma = 1.32

cur_sub = 601
cur_day = 8
cur_type = "HT"

cur_stims = data_yn_clean %>%
      filter(subnum == cur_sub & day == cur_day & type == cur_type) %>%
      select(subnum, day, type, possiblePayoff, reference, yesChosen, rt)

start = Sys.time()
sim_subj_cond_day_once(cur_stims, sampled_sigma, sampled_d, sampled_ndt, sampled_bias)
end = Sys.time()
print(end-start)
```



# Changes in DDM pars

**[THIS ISN'T THE BEST APPROACH. TRY MODELING EACH SUBJECT HIERARCHICALLY INSTEAD]**

### Drift rate

```{r}
fn_draws = paste0(helpers_path, '/inputs/yn_ddm_dRegressions_draws.csv')

if(file.exists(fn_draws)){
  yn_rt_draws = read.csv(fn_draws)
} else{
  subnums = unique(data_yn_clean$subnum)
  
  yn_ddm_draws = data_frame()
  
  for(i in 1:length(subnums)){
    cur_sub = subnums[i]
    
    cur_par_data = all_results_df %>% 
      filter(subnum == cur_sub & par_name == "d")
    
    # REDUCE AMOUNT OF DATA! 100 datapoints per bin
    cur_par_data = cur_par_data %>%
      group_by(type, day) %>%
      sample_n(100)
    
    cur_m <- brm(formula = estimate ~ day * type,
                     data= cur_par_data,
                     warmup = 500,
                     iter = 2500,
                     chains = 4,
                     init = "0",
                     cores = 4,
                     seed = 389253)
    
    cur_draws = as_draws_df(cur_m)
    cur_draws$subnum = cur_sub
    
    yn_ddm_draws = rbind(yn_ddm_draws, cur_draws)
    
  }
  names(yn_ddm_draws) = gsub(":", ".", names(yn_ddm_draws))
  write.csv(yn_ddm_draws, fn_draws, row.names = F)
  
  rm(cur_par_data, cur_m, cur_draws)
}

```

```{r}
yn_par_summary = as.data.frame(yn_ddm_draws) %>%
  select("b_day" ,"b_typeRE", "b_day.typeRE", subnum) %>%
  gather(key, value, -subnum) %>%
  mutate(key = ifelse(key == "b_day", "Day", ifelse(key == "b_typeRE", "Type (RE)", ifelse(key == "b_day.typeRE", "Day * Type (RE)", NA))),
         key = factor(key, levels = c("Type (RE)", "Day", "Day * Type (RE)"))) %>%
  group_by(subnum, key) %>%
  summarise(.groups = 'keep',
            m = mean(value),
            l95 = HDInterval::hdi(value)[1],
            h95 = HDInterval::hdi(value)[2]) %>%
  mutate(subnum = as.factor(subnum),
         task = "Y/N") 
```

```{r}
plim = max(abs(yn_par_summary$l95), yn_par_summary$h95)

p = yn_par_summary %>%
  ggplot(aes(m, subnum)) +
  geom_vline(aes(xintercept = 0), color = "light gray") + 
  geom_point(position = position_dodge(width=.75))+
  geom_errorbarh(aes(xmin = l95, xmax = h95, height=.2), position = position_dodge(width=.75))+
  facet_grid(.~key) +
  labs(x = "Parameter Estimate", y = "Subject", color = "", title = "95% HDI for posterior slopes - d ~ Day * Type") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks = c(0), limits = c(-plim, plim))

p
# ggsave(file=paste0(fig_out_path, 'yn_ddmD_parEsts.jpg'), p, height = 3, width = 7, units="in")

```

### Sigma

```{r}
fn_draws = paste0(helpers_path, '/inputs/yn_ddm_sigmaRegressions_draws.csv')

if(file.exists(fn_draws)){
  yn_rt_draws = read.csv(fn_draws)
} else{
  subnums = unique(data_yn_clean$subnum)
  
  yn_ddm_draws = data_frame()
  
  for(i in 1:length(subnums)){
    cur_sub = subnums[i]
    
    cur_par_data = all_results_df %>% 
      filter(subnum == cur_sub & par_name == "sigma")
    
    # REDUCE AMOUNT OF DATA! 100 datapoints per bin
    cur_par_data = cur_par_data %>%
      group_by(type, day) %>%
      sample_n(100)
    
    cur_m <- brm(formula = estimate ~ day * type,
                     data= cur_par_data,
                     warmup = 500,
                     iter = 2500,
                     chains = 4,
                     init = "0",
                     cores = 4,
                     seed = 389253)
    
    cur_draws = as_draws_df(cur_m)
    cur_draws$subnum = cur_sub
    
    yn_ddm_draws = rbind(yn_ddm_draws, cur_draws)
    
  }
  names(yn_ddm_draws) = gsub(":", ".", names(yn_ddm_draws))
  write.csv(yn_ddm_draws, fn_draws, row.names = F)
  
  rm(cur_par_data, cur_m, cur_draws)
}

```

```{r}
yn_par_summary = as.data.frame(yn_ddm_draws) %>%
  select("b_day" ,"b_typeRE", "b_day.typeRE", subnum) %>%
  gather(key, value, -subnum) %>%
  mutate(key = ifelse(key == "b_day", "Day", ifelse(key == "b_typeRE", "Type (RE)", ifelse(key == "b_day.typeRE", "Day * Type (RE)", NA))),
         key = factor(key, levels = c("Type (RE)", "Day", "Day * Type (RE)"))) %>%
  group_by(subnum, key) %>%
  summarise(.groups = 'keep',
            m = mean(value),
            l95 = HDInterval::hdi(value)[1],
            h95 = HDInterval::hdi(value)[2]) %>%
  mutate(subnum = as.factor(subnum),
         task = "Y/N") 
```

```{r}
plim = max(abs(yn_par_summary$l95), yn_par_summary$h95)

p = yn_par_summary %>%
  ggplot(aes(m, subnum)) +
  geom_vline(aes(xintercept = 0), color = "light gray") + 
  geom_point(position = position_dodge(width=.75))+
  geom_errorbarh(aes(xmin = l95, xmax = h95, height=.2), position = position_dodge(width=.75))+
  facet_grid(.~key) +
  labs(x = "Parameter Estimate", y = "Subject", color = "", title = "95% HDI for posterior slopes - sigma ~ Day * Type") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks = c(0), limits = c(-plim, plim))

p
# ggsave(file=paste0(fig_out_path, 'yn_ddmSigma_parEsts.jpg'), p, height = 3, width = 7, units="in")

```

### Bias

```{r}
fn_draws = paste0(helpers_path, '/inputs/yn_ddm_biasRegressions_draws.csv')

if(file.exists(fn_draws)){
  yn_rt_draws = read.csv(fn_draws)
} else{
  subnums = unique(data_yn_clean$subnum)
  
  yn_ddm_draws = data_frame()
  
  for(i in 1:length(subnums)){
    cur_sub = subnums[i]
    
    cur_par_data = all_results_df %>% 
      filter(subnum == cur_sub & par_name == "bias")
    
    # REDUCE AMOUNT OF DATA! 100 datapoints per bin
    cur_par_data = cur_par_data %>%
      group_by(type, day) %>%
      sample_n(100)
    
    cur_m <- brm(formula = estimate ~ day * type,
                     data= cur_par_data,
                     warmup = 500,
                     iter = 2500,
                     chains = 4,
                     init = "0",
                     cores = 4,
                     seed = 389253)
    
    cur_draws = as_draws_df(cur_m)
    cur_draws$subnum = cur_sub
    
    yn_ddm_draws = rbind(yn_ddm_draws, cur_draws)
    
  }
  names(yn_ddm_draws) = gsub(":", ".", names(yn_ddm_draws))
  write.csv(yn_ddm_draws, fn_draws, row.names = F)
  
  rm(cur_par_data, cur_m, cur_draws)
}

```

```{r}
yn_par_summary = as.data.frame(yn_ddm_draws) %>%
  select("b_day" ,"b_typeRE", "b_day.typeRE", subnum) %>%
  gather(key, value, -subnum) %>%
  mutate(key = ifelse(key == "b_day", "Day", ifelse(key == "b_typeRE", "Type (RE)", ifelse(key == "b_day.typeRE", "Day * Type (RE)", NA))),
         key = factor(key, levels = c("Type (RE)", "Day", "Day * Type (RE)"))) %>%
  group_by(subnum, key) %>%
  summarise(.groups = 'keep',
            m = mean(value),
            l95 = HDInterval::hdi(value)[1],
            h95 = HDInterval::hdi(value)[2]) %>%
  mutate(subnum = as.factor(subnum),
         task = "Y/N") 
```

```{r}
plim = max(abs(yn_par_summary$l95), yn_par_summary$h95)

p = yn_par_summary %>%
  ggplot(aes(m, subnum)) +
  geom_vline(aes(xintercept = 0), color = "light gray") + 
  geom_point(position = position_dodge(width=.75))+
  geom_errorbarh(aes(xmin = l95, xmax = h95, height=.2), position = position_dodge(width=.75))+
  facet_grid(.~key) +
  labs(x = "Parameter Estimate", y = "Subject", color = "", title = "95% HDI for posterior slopes - bias ~ Day * Type") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks = c(0), limits = c(-plim, plim))

p
# ggsave(file=paste0(fig_out_path, 'yn_ddmBias_parEsts.jpg'), p, height = 3, width = 7, units="in")

```

### NDT

```{r}
fn_draws = paste0(helpers_path, '/inputs/yn_ddm_ndtRegressions_draws.csv')

if(file.exists(fn_draws)){
  yn_rt_draws = read.csv(fn_draws)
} else{
  subnums = unique(data_yn_clean$subnum)
  
  yn_ddm_draws = data_frame()
  
  for(i in 1:length(subnums)){
    cur_sub = subnums[i]
    
    cur_par_data = all_results_df %>% 
      filter(subnum == cur_sub & par_name == "ndt")
    
    # REDUCE AMOUNT OF DATA! 100 datapoints per bin
    cur_par_data = cur_par_data %>%
      group_by(type, day) %>%
      sample_n(100)
    
    cur_m <- brm(formula = estimate ~ day * type,
                     data= cur_par_data,
                     warmup = 500,
                     iter = 2500,
                     chains = 4,
                     init = "0",
                     cores = 4,
                     seed = 389253)
    
    cur_draws = as_draws_df(cur_m)
    cur_draws$subnum = cur_sub
    
    yn_ddm_draws = rbind(yn_ddm_draws, cur_draws)
    
  }
  names(yn_ddm_draws) = gsub(":", ".", names(yn_ddm_draws))
  write.csv(yn_ddm_draws, fn_draws, row.names = F)
  
  rm(cur_par_data, cur_m, cur_draws)
}

```

```{r}
yn_par_summary = as.data.frame(yn_ddm_draws) %>%
  select("b_day" ,"b_typeRE", "b_day.typeRE", subnum) %>%
  gather(key, value, -subnum) %>%
  mutate(key = ifelse(key == "b_day", "Day", ifelse(key == "b_typeRE", "Type (RE)", ifelse(key == "b_day.typeRE", "Day * Type (RE)", NA))),
         key = factor(key, levels = c("Type (RE)", "Day", "Day * Type (RE)"))) %>%
  group_by(subnum, key) %>%
  summarise(.groups = 'keep',
            m = mean(value),
            l95 = HDInterval::hdi(value)[1],
            h95 = HDInterval::hdi(value)[2]) %>%
  mutate(subnum = as.factor(subnum),
         task = "Y/N") 
```

```{r}
plim = max(abs(yn_par_summary$l95), yn_par_summary$h95)

p = yn_par_summary %>%
  ggplot(aes(m, subnum)) +
  geom_vline(aes(xintercept = 0), color = "light gray") + 
  geom_point(position = position_dodge(width=.75))+
  geom_errorbarh(aes(xmin = l95, xmax = h95, height=.2), position = position_dodge(width=.75))+
  facet_grid(.~key) +
  labs(x = "Parameter Estimate", y = "Subject", color = "", title = "95% HDI for posterior slopes - ndt ~ Day * Type") +
  theme(legend.position = "bottom",
        panel.grid = element_blank(),
        legend.box.margin=margin(t = -10))+
  scale_x_continuous(breaks = c(0), limits = c(-plim, plim))

p
# ggsave(file=paste0(fig_out_path, 'yn_ddmNDT_parEsts.jpg'), p, height = 3, width = 7, units="in")

```

